---
title: "R Notebook"
output: html_notebook
---

```{r}
pacman::p_load(
  tidyverse,
  deSolve)
```

# model
## structure
```{r}
lv <- function(times, state, parms) {
  with(as.list(c(state, parms)), {
# moose
    Consumption    <- ((a * Pyoung)/(1 + a * h * Pyoung)) * Moose
    Death <- lM * (Moose^2)
    
    # palatable 
    GrowthPy <- rPy * Pyoung * (1 - (Pyoung + Pmature + alphaUPy * Unpal)/kPy)
    NewSeed <- s * Pmature
    DeathPy <- lPy * Pyoung
    GrowthPm <- rPm * Pmature * (1 - (Pyoung + Pmature + alphaUPm * Unpal)/kPm)
    Ageing <- g*(g^(3*(Consumption)/(Pyoung+0.01))) * Pyoung #need to add small amount to Pyoung in denominator
    DeathPm <- lPm * Pmature
    
    # unpalatable
    GrowthU <- rU * Unpal * (1 - (alphaPyU * Pyoung + alphaPmU * Pmature + Unpal)/kU)
    DeathU <- lU * Unpal

    # odes
    dMoose  <- Consumption*e - Death 
    dPyoung <- GrowthPy + NewSeed - Consumption - Ageing - DeathPy
    dPmature <- GrowthPm + Ageing - DeathPm
    dUnpal <- GrowthU - DeathU
    

    list(c(dMoose, dPyoung, dPmature, dUnpal))
  })
}
```

## parameters
```{r}
parms  <- c(a = 0.9985, 
            h = 0.0223,
            e = 0.02,
            lM = 0.3234,
            rPy = 0.2,
            rPm = 0.14,
            s = 0.011,
            alphaUPy = 0.001,
            alphaUPm = 0.0001, 
            kPy = 1000,
            kPm = 68000, 
            g = 0.133,
            lPm = 0.01,
            lPy = 0.2,
            rU = 0.9,
            alphaPyU = 0.002, 
            alphaPmU = 0.006, 
            kU = 900,
            lU = 0.4)
```

## initial conditions
```{r}

y_0 <- c(Moose =2, Pyoung = 50, Pmature = 0, Unpal = 100)
```

## extinction
```{r}
eps <- 1e-2
## event triggered if state variable <= eps
eventfun <- function(times, y, parms) {
  y[which(y<eps | y<0)] <- 0 
  return(y)
}
```

## time
```{r}
time_vec1 <- seq(from = 1, to = 600, length.out = 600)
```


## run model
```{r}

out2 <- ode(y = y_0, times = time_vec1, func = lv, parms = parms, method = "lsode", events=list(func = eventfun, time = time_vec1), atol = 1e-21)

```

## function to run model over different conditions
```{r}
ode_reps <- function(parameters, initial_conditions) {
  out <- ode(y = initial_conditions, times = time_vec1, func = lv, parms = parameters, events=list(func = eventfun, time = time_vec1), method = "lsode", atol = 1e-21)
}
```


# ranges

## initial conditions
```{r}
# make dataframe with sequence of initial conditions to sample over
# always starting from no mature and some level of unpal
# smallest values 0 for both, moose up to 6 Mg moose, and 500 Py

n_i <- 8

M_init <- seq(0, 6, length.out = n_i)
Py_init <- seq(0, 300, length.out = n_i) 
Pm_init <- rep(0, n_i)
U_init <- rep(100, n_i)

init_seq <- data.frame(Moose=rep(M_init, each = n_i), Pyoung = rep(Py_init, n_i), Pmature = rep(Pm_init,n_i), Unpal = rep(U_init,n_i))

y_0d <- split(as.matrix(init_seq), row(init_seq)) %>% 
  lapply(setNames, nm = c("Moose", "Pyoung", "Pmature", "Unpal"))

y_0d_id <- as.data.frame(t(as.data.frame(y_0d))) %>% 
  mutate(id = seq(1, length(y_0d), by = 1))
```

## parameters
```{r}
# make datafram with distribution of parameters

LVlow <-  c(0.996, #a
            0.0207933, # h
            0.01, #e
            0.2647, # lM
            0.15, #rPy
            0.1, #rPm
            0.0088, #s
            0.0005, #alphaUPy
            0.000, #alphaUPm
            400, #kPy
            20000, # kPm
            0.09, # g
            0.005, #lPm
            0.1, #lPy
            0.6,#rU
            0.001, # alphaPyU
            0.004, # alphaPmU
            300, #kU
            0.168) #lU

LVhigh <-  c(1.005, #a
            0.038735, # h
            0.03, #e
            0.3765, # lM
            0.325, #rPy
            0.2, #rPm
            0.053, #s
            0.002, #alphaUPy
            0.0002, #alphaUPm
            2000, #kPy
            80000, # kPm
            0.2, # g
            0.06, #lPm
            0.3, #lPy
            1.3 ,#rU
            0.003, # alphaPyU
            0.008, # alphaPmU
            1200, #kU
            1) #lU


param_dist <- data.frame(min = LVlow, max = LVhigh, mean = parms)

library(truncnorm)
```

### how many samples
number of parameter combos vs number recovered
```{r}
## for n samples of random parameter combos vs n recover



# make list of number of sampls to try
n_p_list <- as.list(rgamma(100, 4, 0.0175), 1000)

n_p_list2 <- list(6, 12, 20)

# function to repeat ode across initial conditions and each combination of parameters, for each number of samples in list 
rep_over_n_param_samples <- function (n_param) {
  
# make n random combinations of paramaters
  n_p <- n_param
  sampled_param <- list()
  
# sample from distribution of each parameter n times
  for(i in rownames(param_dist)){
    sampled_param[[i]] <- signif(rtruncnorm(n=n_p, a=param_dist[[i,1]], b=param_dist[[i,2]], mean=param_dist[[i,3]]), 4)
  }

# make list of possible parameter combinations
  sampled_param_list <-  split(as.matrix(as.data.frame(sampled_param)), row(as.data.frame(sampled_param))) %>% 
    lapply(setNames, nm = names(parms))
  
  sampled_param_list_final <- list()
  # remove combinations that don't meet assumptions (around competative effects, growth rates, carrying capacities, and death rates)
  
  # relative growth rate
  sampled_param_list2 <-  sampled_param_list[sapply(sampled_param_list, `[`, 'rPy') < sapply(sampled_param_list, `[`, 'rU') & sapply(sampled_param_list, `[`, 'rPm') < sapply(sampled_param_list, `[`, 'rPy')]
  
  # competative effects
  sampled_param_list3 <-  sampled_param_list2[sapply(sampled_param_list2, `[`, 'alphaUPm') < sapply(sampled_param_list2, `[`, 'alphaUPy') & sapply(sampled_param_list2, `[`, 'alphaUPy') < sapply(sampled_param_list2, `[`, 'alphaPyU') & sapply(sampled_param_list2, `[`, 'alphaPyU') < sapply(sampled_param_list2, `[`, 'alphaPmU')]
  
  # carrying capacities
  sampled_param_list4 <-  sampled_param_list3[sapply(sampled_param_list3, `[`, 'kU') < sapply(sampled_param_list3, `[`, 'kPy') & sapply(sampled_param_list3, `[`, 'kPy') < sapply(sampled_param_list3, `[`, 'kPm')]
  
  # loss
  sampled_param_list_final <-  sampled_param_list4[sapply(sampled_param_list4, `[`, 'lPm') < sapply(sampled_param_list4, `[`, 'lU')]

# combine with initial values (constant) 
  args <- expand.grid(
    parameters=sampled_param_list_final,
    initial_conditions=y_0d) 
  args_id <- args %>% mutate(id = seq(1, nrow(args), by = 1))
  list2env(args, envir=.GlobalEnv)
  
# run ode
  args$output <- mapply(ode_reps, parameters, initial_conditions, SIMPLIFY = F)
  names(args$output) <- seq(1, nrow(args_id), by = 1)
  
# remove runs that didn't go
  args_less <- purrr::discard(args$output, ~nrow(.) < 3)
  arg_less_last <- lapply(args_less,tail, 1, SIMPLIFY = T) 
  
# classify as recovered or not
  names(arg_less_last) <- paste(names(arg_less_last), ifelse(map(arg_less_last, pluck, 4) > 0, "forest", "grassland"))

# add info on initial conditions
  g_vs_f <- data.frame(id = parse_number(names(arg_less_last)), g_or_f = str_remove_all(names(arg_less_last), "[:digit:]")) %>% 
    left_join(args_id) %>% 
   mutate(Moose = unlist(map(initial_conditions, pluck, 1)), By = unlist(map(initial_conditions, pluck, 2))) %>% 
    select(!c(1,3,4))

# count number of recoveries
  n_g_vs_f <- g_vs_f %>% 
   group_by(as.factor(Moose), as.factor(By), as.factor(g_or_f), .drop=FALSE) %>% 
   count(.drop=FALSE) %>% 
   ungroup() %>% 
   mutate(Moose = as.numeric(as.character(`as.factor(Moose)`))) %>% 
   mutate(By = as.numeric(as.character(`as.factor(By)`))) %>% 
   rename(g_or_f = `as.factor(g_or_f)`) %>% 
   select(c(3:6))

# count total number recovered for all simulations relative to number of simulations
  percent_rec <- sum(filter(n_g_vs_f, g_or_f == " forest")$n)/sum(n_g_vs_f$n)
  
  return(percent_rec)
}

# run function
n_p_recoveries <- lapply(n_p_list2, rep_over_n_param_samples)

plot(n_p_list2, n_p_recoveries)
```

### list for heatmap
```{r}
sampled_param <- list()

n_p <- 6 # may change

for(i in rownames(param_dist)){
sampled_param[[i]] <- signif(rtruncnorm(n=n_p, a=param_dist[[i,1]], b=param_dist[[i,2]], mean=param_dist[[i,3]]), 4)
}

sampled_param_list <-  split(as.matrix(as.data.frame(sampled_param)), row(as.data.frame(sampled_param))) %>% 
  lapply(setNames, nm = names(parms))

sampled_param_list_final <- list()
sampled_param_list_final[[1]] <- parms
sampled_param_list_final[[2]] <- parms
sampled_param_list_final[[1]] <- sampled_param_list[[1]]

# remove combinations that don't meet assumptions (around competative effects, growth rates, carrying capacities, and death rates)

# relative growth rate
sampled_param_list2 <-  sampled_param_list[sapply(sampled_param_list, `[`, 'rPy') < sapply(sampled_param_list, `[`, 'rU') & sapply(sampled_param_list, `[`, 'rPm') < sapply(sampled_param_list, `[`, 'rPy')]

# competative effects
sampled_param_list3 <-  sampled_param_list2[sapply(sampled_param_list2, `[`, 'alphaUPm') < sapply(sampled_param_list2, `[`, 'alphaUPy') & sapply(sampled_param_list2, `[`, 'alphaUPy') < sapply(sampled_param_list2, `[`, 'alphaPyU') & sapply(sampled_param_list2, `[`, 'alphaPyU') < sapply(sampled_param_list2, `[`, 'alphaPmU')]

# carrying capacities
sampled_param_list4 <-  sampled_param_list3[sapply(sampled_param_list3, `[`, 'kU') < sapply(sampled_param_list3, `[`, 'kPy') & sapply(sampled_param_list3, `[`, 'kPy') < sapply(sampled_param_list3, `[`, 'kPm')]

# loss
sampled_param_list_final <-  sampled_param_list4[sapply(sampled_param_list4, `[`, 'lPm') < sapply(sampled_param_list4, `[`, 'lU')]
```


# effect of initial conditions

## heatmap
```{r}
## give some result at each step so know loops aren't getting stuck
pacman::p_load(
  tidyverse,
  deSolve)
# make ode into function where parameters and initial conditions can be used
out_end <- list()                     
out <- list()        

# make all combinations availabel in environment
args <- expand.grid(
  parameters=sampled_param_list_final,
  initial_conditions=y_0d) 
args_id <- args %>% mutate(id = seq(1, nrow(args), by = 1))
list2env(args, envir=.GlobalEnv)

# run over params and init conditions
args$output <- mapply(ode_reps, parameters, initial_conditions, SIMPLIFY = F)

# give simulations names based params and init conditions
names(args$output) <- seq(1, nrow(args_id), by = 1)

# remove any simulations that didnt run properly
args_less <- purrr::discard(args$output, ~nrow(.) < 3)
arg_removed <- purrr::keep(args$output, ~nrow(.) < 3)


# # look at coefficient of variation for last 25 years
# cv <- function(x)  sd(x)/mean(x)
# 
# # select only one column of 
# arg_last_25M_l <- lapply(lapply(args_less,tail, 25, SIMPLIFY = T), "[", , 'Moose')
# arg_last_25Py_l <- lapply(lapply(args_less,tail, 25, SIMPLIFY = T), "[", , 'Pyoung')
# arg_last_25Pm_l <- lapply(lapply(args_less,tail, 25, SIMPLIFY = T), "[", , 'Pmature')
# arg_last_25U_l <- lapply(lapply(args_less,tail, 25, SIMPLIFY = T), "[", , 'Unpal')
# 
# arg_last_25_l <- list(arg_last_25M_l, arg_last_25Py_l, arg_last_25Pm_l, arg_last_25U_l)
# 
# arg_cv_l <- lapply(arg_last_25_l, lapply, cv)
# 
# library(rlist)
# 
# # return any that are above some cut off (10e-7 for now)
# arg_cv_less_l <- lapply(arg_cv_l, list.filter, . >= 10e-7)
# 
# 
# arg_cv_less_cv <- args_less[ ! names(args_less) %in% names(arg_cv_less_l[[1]]) ]
# 
# # get final stocks from remaining simulations
arg_less_last <- lapply(args_less,tail, 1, SIMPLIFY = T)

# make this info a heat map

# if pmature = 0, and/or Unpal ≠ 0 then grassland
# if pmature ≠ 0 then forest

names(arg_less_last) <- paste(names(arg_less_last), ifelse(map(arg_less_last, pluck, 4) > 0, "forest", "grassland"))

# add info on initial conditions
g_vs_f <- data.frame(id = parse_number(names(arg_less_last)), g_or_f = str_remove_all(names(arg_less_last), "[:digit:]")) %>% 
  left_join(args_id) %>% 
  mutate(Moose = unlist(map(initial_conditions, pluck, 1)), By = unlist(map(initial_conditions, pluck, 2))) %>% 
  select(!c(1,3,4))

# count number of recoveries
n_g_vs_f <- g_vs_f %>% 
  group_by(as.factor(Moose), as.factor(By), as.factor(g_or_f), .drop=FALSE) %>% 
  count(.drop=FALSE) %>% 
  ungroup() %>% 
  mutate(Moose = as.numeric(as.character(`as.factor(Moose)`))) %>% 
  mutate(By = as.numeric(as.character(`as.factor(By)`))) %>% 
  rename(g_or_f = `as.factor(g_or_f)`) %>% 
  select(c(3:6))

# into %
n_f <- subset(n_g_vs_f, g_or_f == " forest") %>% 
  mutate(percent_recover = (n/length(sampled_param_list_final))*100)

# mark 50/50

library(viridis)

n_f2 <- n_f %>% 
  filter(percent_recover >= 50) %>% 
  group_by(Moose,  .drop=FALSE) %>% 
  filter(By == min(By)) %>%
  mutate(Moose = Moose - 0.2068966/2, By = By - 10.34483/2	) %>%
  arrange(Moose)

n_f2 <- n_f2 %>% bind_rows(n_f2[nrow(n_f2), ] %>% mutate(Moose = Moose))
n_f2

# make heatmap
heatmap_moose_By <- ggplot() +
  geom_tile(data = n_f, aes(x = Moose, y = By, fill = percent_recover)) +
  geom_step(data = n_f2, aes(x = Moose, y = By), size = 0.5) +
  scale_fill_gradient2(high = "#4D8F26", low = "#f29414", mid = "#f3f59e", midpoint = 50) +
  labs(x = "Moose biomass (Metric tons)", y = "Young palatable plant biomass (Metric tons)", fill = "Percent\nrecovered") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(- 10.34483/2, 300)) +
  scale_x_continuous(expand = c(0,0))+ theme(legend.position="top")

heatmap_moose_By


```

## time for recovered to recover
```{r}
args_less2 <- args_less
names(args_less2) <- names(arg_less_last)


# remove any that go to grassland
args_recover <- args_less2[ ! names(args_less2) %>% str_detect("grassland") ]

# function
return_year_stable_delta <- function(odes) {

  args_recover_delta <- as.data.frame(odes) %>% 
  mutate(dMoose = Moose - lag(Moose), dPyoung = Pyoung - lag(Pyoung), dPmature = Pmature - lag(Pmature), dUnpal = Unpal - lag(Unpal)) %>% 
  filter(if_all(c(6:9), ~. <= 1e-8 | is.nan(.)))
  
  args_recover_deltayr <- args_recover_delta[1,1]
  return(args_recover_deltayr)
}

library(zoo)

# function
return_year_stable_cv <- function(odes) {
  test_rollcv <- rollapply(odes, width=10, FUN=cv, fill=NA, by.column = T)
  
  test_rollcv_stop <- test_rollcv %>% 
    as.data.frame() %>% 
    mutate(time = rownames(.)) %>% 
    filter(if_all(c(2:5), ~. <= 0.001 | is.nan(.))) # change this to be more in line with rootSolve and deSolve steady state criteria
  
  test_rollcv_stopyr <- test_rollcv_stop[1,1]
  return(test_rollcv_stopyr)
}

cv <- function(x)  sd(x)/mean(x)

year_stable_delta <- lapply(args_recover, return_year_stable_delta)

# there are some that just take a long time to reach stable (because unpal very slowly going towards 0 and mature slowly reaching closer to carrying cap, same outcome with cv

# add to simulation data
f_yr <- data.frame(id = parse_number(names(year_stable_delta)), g_or_f = str_remove_all(names(year_stable_delta), "[:digit:]"), year = unlist(year_stable_delta)) %>% 
  left_join(args_id) %>% 
  mutate(Moose = unlist(map(initial_conditions, pluck, 1)), By = unlist(map(initial_conditions, pluck, 2))) %>% 
  na.omit() %>% 
  select(!c(1,4,5))
# seems to depend mostly on parameter

avg_yr_f <- f_yr %>% 
  group_by(as.factor(Moose), as.factor(By), .drop = F) %>% 
  summarise(mean_yr = mean(as.numeric(year))) %>% 
  ungroup() %>% 
  mutate(Moose = as.numeric(as.character(`as.factor(Moose)`))) %>% 
  mutate(By = as.numeric(as.character(`as.factor(By)`))) %>% 
  select(c(3:5))

avg_yr_50_f <- avg_yr_f %>% 
  right_join(filter(n_f, percent_recover >= 0))
  
n_f22100 <- avg_yr_50_f %>% 
  filter(percent_recover >= 100) %>% 
  group_by(Moose,  .drop=FALSE) %>% 
  filter(By == min(By)) %>%
  mutate(Moose = Moose - 0.2068966/2, By = By - 10.34483/2	) %>%
  arrange(Moose)

n_f22100 <- n_f22100 %>% bind_rows(n_f22100[nrow(n_f22100), ] %>% mutate(Moose = Moose))

# seperate colur scheme for time

heatmap_yr_f <- ggplot() +
  geom_tile(data = avg_yr_50_f, aes(x = Moose, y = By, fill = mean_yr)) +
  scale_fill_gradient(low = "#421650", high = "white", na.value = "#C4C4C4") +
  labs(x = "Moose biomass (Metric tons)", y = "Young palatable plant biomass (Metric tons)", fill = "Years to\nrecover") +
  theme_classic() +
  scale_y_continuous(expand = c(0, 0), limits = c(- 10.34483/2, 300)) +
  scale_x_continuous(expand = c(0,0))



heatmap_yr_f
```


# effect of parameters

## functions
```{r}
# to repeat ode over initial conditions and parameter values with one parameter set
ode_fvsg <- function(param_list_error) {
  out_param2 <- lapply(y_0d, ode_reps, parameters = param_list_error)
  
  names(out_param2) <- seq(1, length(y_0d), by = 1)
  out_param_less2 <- purrr::discard(out_param2, ~nrow(.) < 3)
  out_param_less_last2 <- lapply(out_param_less2,tail, 1, SIMPLIFY = T) 
  
  names(out_param_less_last2) <- paste(names(out_param_less_last2), ifelse(map(out_param_less_last2, pluck, 4) > 0, "forest", "grassland"))
  
  
  g_vs_f_param2 <- data.frame(id = parse_number(names(out_param_less_last2)), g_or_f = str_remove_all(names(out_param_less_last2), "[:digit:]")) %>% 
    left_join(y_0d_id) %>% 
    mutate(Moose = unlist(map(y_0d, pluck, 1)), By = unlist(map(y_0d, pluck, 2))) %>% 
    select(!c(1,4,5,6))
  
  
  return(g_vs_f_param2)
}

# to calculate percent recovered
percent_recover_param <- function(x) {
  df_list <- list()
  n_rec_list <- list()
  for(i in 1:ncol(x)){
  df_list[[i]] <- as.data.frame(do.call(cbind, x[,i]))
  n_rec_list[[i]] <- nrow(filter(df_list[[i]], g_or_f == " forest"))/nrow(df_list[[i]])
  }
  return(n_rec_list)
}

# to run above and create graph
param_recovery <- function(parameter){

  param_list <- list(rep(list(),11))

  value_list <- as.list(signif(seq(from = param_dist[parameter,'min'], to = param_dist[parameter,'max'], by = (param_dist[parameter,'max'] - param_dist[parameter,'min'])/10),4))

  for(i in 1:length(value_list)){
   param_list[[i]] <- sampled_param_list_final
    for(j in 1:length(sampled_param_list_final)){
     param_list[[i]][[j]][[parameter]] <- value_list[[i]]
    }
  }

  g_vs_f <- lapply(param_list, sapply, ode_fvsg)

  g_vs_f_recover <- lapply(g_vs_f, percent_recover_param)
  names(g_vs_f_recover) <- value_list

  recover_df <- as.data.frame(do.call(rbind, g_vs_f_recover)) %>% 
   mutate(parameter = rownames(.)) %>% 
    mutate(across(contains("V"), ~ unlist(.))) %>% 
   pivot_longer(cols = !c("parameter"), names_to = "rep", values_to = "recover")


  return(recover_df)
}

plot_effect_param <- function(data) {
 ggplot(data, aes(x = parameter, y = recover, colour = recover)) +
  geom_violin() +
  geom_jitter(width = 0.05, height = 0, size = 1) +
  scale_color_viridis() +
  geom_point(stat = 'summary', fun = 'mean', size = 2) 
}
```

## across list of parameters
```{r}
pacman::p_load(
  tidyverse,
  deSolve)

parms_sub <- parms[c('e')]
ode_recovery <- lapply(names(parms_sub), param_recovery)

# check if change over values of parameter (cv?), for mean and upper and lower quantiles?
cv_for_recovery <- function(recover_df) {
recover_df_cv <- recover_df %>% 
  group_by(parameter) %>% 
  summarise(mean = mean(recover), q1 = quantile(recover, 0.25), q3 = quantile(recover, 0.75)) %>% 
  summarise(cv_m = cv(mean), cv_q1 = cv(q1), cv_q3 = cv(q3))
return(recover_df_cv)
}

ode_recovery_change <- lapply(names(parms_sub), cv_for_recovery)
```


## time to recovery based on parameters
```{r}
# function to get time to recovery
param_time_rec <- function(param_list_error) {
  out_param2 <- lapply(y_0dz2, ode_reps, parameters = param_list_error)
  
  names(out_param2) <- seq(1, length(y_0dz2), by = 1)
  out_param_less2 <- purrr::discard(out_param2, ~nrow(.) < 3)
  
  out_param_less_last2 <- lapply(out_param_less2,tail, 1, SIMPLIFY = T) 
  
  names(out_param_less2) <- paste(names(out_param_less_last2), ifelse(map(out_param_less_last2, pluck, 4) > 0, "forest", "grassland"))
  
  args_recover <- out_param_less2[ ! names(out_param_less2) %>% str_detect("grassland") ]
  
  args_recover_yr <- lapply(args_recover, return_year_stable_delta)
  
  args_recover_yravg <- mean(as.numeric(args_recover_yr))
  
  return(args_recover_yravg)
}

# to return year stable for each parameter and plot

return_year_stable_param <- function(param) {
  param_listat <- list(rep(list(),11))
  
  value_listat <- as.list(signif(seq(from = param_dist[param,'min'], to = param_dist[param,'max'], by = (param_dist[param,'max'] - param_dist[param,'min'])/10),4))
  
  for(i in 1:length(value_listat)){
    param_listat[[i]] <- sampled_param_list_final[seq(1, length(sampled_param_list_final), 10)] # will not be seq for full simulation
    for(j in 1:length(sampled_param_list_final[seq(1, length(sampled_param_list_final), 10)])){
      param_listat[[i]][[j]][['a']] <- value_listat[[i]]
    }
  }
  
  gf_param_yr <- lapply(param_listat, sapply, param_time_rec) 
  names(gf_param_yr) <- value_listat
  
  
  gf_param_yrdf <- as.data.frame(do.call(rbind, gf_param_yr)) %>% 
    mutate(parameter = rownames(.)) %>% 
    pivot_longer(cols = !c("parameter"), names_to = "rep", values_to = "yr_recover")
  
  param_plot <- ggplot(gf_param_yrdf, aes(x = parameter, y = yr_recover, colour = yr_recover)) +
  geom_violin() +
  geom_jitter(width = 0.1, height = 0, size = 1) +
  scale_color_viridis(direction = -1) +
  geom_point(stat = 'summary', fun = 'mean', size = 2)
}


param_recovery <- lapply(names(parms), return_year_stable_param)
```



