---
title: "4) Run ode over parameters"
author: "Anonymous"
date: "2024-08-27"
output: html_document
---

#libraries
```{r}
pacman::p_load(
  tidyverse,
  deSolve,
  parallel,
  pbapply,
  future.apply,
  progressr)
```

# source code
```{r}
source(knitr::purl("~/code availability/5) Parameter functions.Rmd", quiet=TRUE))  ###PATH NAME###
# will source model structure and as well
```


```{r}
y_0d_par <- readRDS(file = "~/code availability/outputs/y_0d_par.RDS")  ###PATH NAME###

y_0d_par_id <- as.data.frame(t(as.data.frame(y_0d_par))) %>% 
  mutate(id = seq(1, length(y_0d_par), by = 1))
```


# run sequence of functions
that give all outputs
takes a long time and uses a lot of memory so can only run a few parameters at a time
need to restart R or clear unused memory, then rerun chunks above, between each lapply

```{r}
#lapply(list(1,2, 3), param_effect_sequence)

#lapply(list(4, 5, 6), param_effect_sequence)

#lapply(list(7, 8, 9), param_effect_sequence)

# lapply(list(10, 11, 12), param_effect_sequence)

#lapply(list(13, 14, 15), param_effect_sequence)

#lapply(list(16, 17, 18, 19), param_effect_sequence)
```

# plot outputs

## individual plots
to see which have impact

### percent recover
```{r}
plot_param_rec('a', expression('l'[M]*' ((t'[M]*' * year )'^-1*')')) # visually little effect
plot_param_rec('e', expression('e (t'[M]*' * t'[Py]^-1*')'))
plot_param_rec_noy('h', expression('h (t'[M]*' * year * t'[Py]^-1*')'))
plot_param_rec_noy('lM', expression('l'[M]*' ((t'[M]*' * year )'^-1*')'))
plot_param_rec_noy('rPm', 'units') #  visually little effect
plot_param_rec_noy('rPy', 'units')
plot_param_rec_noy('s', 'units') # no change
plot_param_rec_noy('alphaUPm', 'units') # no change
plot_param_rec_noy('alphaUPy', 'units') # no change
plot_param_rec_noy('kPy', 'units') #  visually little effect
plot_param_rec_noy('kPm', 'units') # no change
plot_param_rec_noy('g', 'units')
plot_param_rec_noy('lPm', 'units')#  visually little effect
plot_param_rec_noy('lPy', 'units')
plot_param_rec_noy('rU', 'units')# no change
plot_param_rec_noy('alphaPyU', 'units') # no change
plot_param_rec_noy('alphaPmU', 'units') # no change
plot_param_rec_noy('kU', 'units') # no change
plot_param_rec_noy('lU', 'units') # no change
```

### year recovered
```{r}
# will need to change y axis to include min and max yr over all params
plot_param_rec_yr('a', 'units') # visually little effect
plot_param_rec_yr('e', expression('e (t'[M]*' * t'[Py]^-1*')'))
plot_param_rec_yr_noy('h', expression('h (t'[M]*' * year * t'[Py]^-1*')'))
plot_param_rec_yr_noy('lM', expression('l'[M]*' ((t'[M]*' * year )'^-1*')'))
plot_param_rec_yr('rPm', 'units') 
plot_param_rec_yr('rPy', 'units')
plot_param_rec_yr('s', 'units') 
plot_param_rec_yr('alphaUPm', 'units') # visually little effect
plot_param_rec_yr('alphaUPy', 'units') # visually little effect
plot_param_rec_yr('kPy', 'units') # visually little effect
plot_param_rec_yr('kPm', 'units')
plot_param_rec_yr('g', 'units')
plot_param_rec_yr('lPm', 'units')
plot_param_rec_yr('lPy', 'units') # small change at low but mostly visually little effect
plot_param_rec_yr('rU', 'units') # visually little effect
 plot_param_rec_yr('alphaPyU', 'units') # no change
plot_param_rec_yr('alphaPmU', 'units') # visually little effect
 plot_param_rec_yr('kU', 'units')  # visually little effect
 plot_param_rec_yr('lU', 'units') # visually little effect

```

## plots together
cleaned up version only run for parameters with visual effect above

## percent recovered

### create labels
```{r}
important_param_percent <- list('e', 'h', 'lM', 'rPy', 'g', 'lPy')

param_dfs <- lapply(important_param_percent, df_param_rec)
names(param_dfs) <- important_param_percent

param_df1 <- rbindlist(param_dfs, idcol = T) %>% 
  mutate(.id = factor(.id, c('e', 'h', 'lM', 'rPy', 'g', 'lPy'), labels = c(expression('e (t'[M]*' * t'[Py]^-1*')'), expression('h (t'[M]*' * year * t'[Py]^-1*')'), expression('l'[M]*' ((t'[M]*' * year)'^-1*')'), expression('r'[Py]*'(year'^-1*')'), expression('w (year'^-1*')'), expression('l'[Py]*' (year'^-1*')'))))

param_mean_dfs <- lapply(important_param_percent, df_param_rec_mean)
names(param_mean_dfs) <- important_param_percent

param_mean_df1 <- rbindlist(param_mean_dfs, idcol = T) %>% 
  mutate(.id = factor(.id, c('e', 'h', 'lM', 'rPy', 'g', 'lPy'), labels = c(expression('e (t'[M]*' * t'[Py]^-1*')'), expression('h (t'[M]*' * year * t'[Py]^-1*')'), expression('l'[M]*' ((t'[M]*' * year)'^-1*')'), expression('r'[Py]*'(year'^-1*')'), expression('w (year'^-1*')'), expression('l'[Py]*' (year'^-1*')'))))
```

### plot
```{r}
p_plot_rec <- ggplot() +
    geom_violin(data = param_df1, aes(factor(parameter), recover), size = 0.3) +
  facet_wrap(~.id, labeller = label_parsed, scales = "free_x", strip.position = "bottom") +
    geom_point(data = param_mean_df1, aes(factor(parameter), mean, colour = mean)) +
    theme_classic() +
    scale_x_discrete(expand = c(0.12,0)) +
    labs(x = NULL, y = "Percent regenerated") +
    # rectangle with gradient
    theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8), strip.background = element_blank(), strip.placement = "outside") +
    #scale_colour_gradient(low = "#290934", high = "#C6B9CA")
    scale_color_gradientn(colors = c("#4D8F26", "#f3f59e", "#f29414"), values = c(1, 0.5, 0), limits = c(0, 1)) #+
   # coord_cartesian(clip = "off") +
   # annotation_custom(grid::rectGrob(x = unit(0.008, "npc"), y = unit(0.5, "npc"),
   #                                   width = unit(1, "mm"), height = unit(25, "mm"), gp = gpar(col = NA, fill = grid::linearGradient(colour = c("#f29414", "#f3f59e", "#4D8F26"), stops = c(0, 0.5, 1)), lwd = unit(0.1, "pt"))))

jpeg("~/code availability/outputs/param_percent_rec.jpg", height = 14, width = 16, units = "cm", res = 600)  ###PATH NAME###
p_plot_rec %>%  annotate_figure(left = grid::rectGrob(x = unit(0.008, "npc"), y = unit(0.5, "npc"), width = unit(1, "mm"), height = unit(35.45, "mm"), gp = gpar(col = NA, fill = grid::linearGradient(colour = c("#f29414", "#f3f59e", "#4D8F26"), stops = c(0, 0.5, 1)), lwd = unit(0.1, "pt")), hjust = -18, vjust = 1.035)) %>%  annotate_figure(left = grid::rectGrob(x = unit(0.008, "npc"), y = unit(0.5, "npc"), width = unit(1, "mm"), height = unit(35.45, "mm"), gp = gpar(col = NA, fill = grid::linearGradient(colour = c("#f29414", "#f3f59e", "#4D8F26"), stops = c(0, 0.5, 1)), lwd = unit(0.1, "pt")), hjust = -21.55, vjust = -0.63))

```

## year recovered

### create labels
```{r}
important_param_year <- list('e', 'h', 'lM', 'rPy', 'g', 's', 'rPm', 'kPm', 'lPm')

param_yr_dfs <- lapply(important_param_year, df_param_yr)
names(param_yr_dfs) <- important_param_year

param_yr_df1 <- rbindlist(param_yr_dfs, idcol = T) %>% 
  mutate(.id = factor(.id, c('e', 'h', 'lM', 'rPy', 'g', 's', 'rPm', 'kPm', 'lPm'), labels = c(expression('e (t'[M]*' * t'[Py]^-1*')'), expression('h (t'[M]*' * year * t'[Py]^-1*')'), expression('l'[M]*' ((t'[M]*' * year )'^-1*')'), expression('r'[Py]*' (year'^-1*')'), expression('w (year'^-1*')'), expression('s (t'[Py]*' * (t'[Pm]*' * year)'^-1), expression('r'[Pm]*' (year'^-1*')'), expression('k'[Pm]*' (t'[Pm]*')'), expression('l'[Pm]*' (year'^-1*')'))))

param_yr_mean_dfs <- lapply(important_param_year, df_param_yr_mean)
names(param_yr_mean_dfs) <- important_param_year

param_yr_mean_df1 <- rbindlist(param_yr_mean_dfs, idcol = T) %>% 
  mutate(.id = factor(.id, c('e', 'h', 'lM', 'rPy', 'g', 's', 'rPm', 'kPm', 'lPm'), labels = c(expression('e (t'[M]*' * t'[Py]^-1*')'), expression('h (t'[M]*' * year * t'[Py]^-1*')'), expression('l'[M]*' ((t'[M]*' * year )'^-1*')'), expression('r'[Py]*' (year'^-1*')'), expression('w (year'^-1*')'), expression('s (t'[Py]*' * (t'[Pm]*' * year)'^-1), expression('r'[Pm]*' (year'^-1*')'), expression('k'[Pm]*' (t'[Pm]*')'), expression('l'[Pm]*' (year'^-1*')'))))
```

### plot
```{r}
p_plot_yr <- ggplot() +
    geom_violin(data = param_yr_df1, aes(factor(parameter), recover), size = 0.3) +
  facet_wrap(~.id, labeller = label_parsed, scales = "free_x", strip.position = "bottom") +
    geom_point(data = param_yr_mean_df1, aes(factor(parameter), mean, colour = mean)) +
    theme_classic() +
    scale_x_discrete(expand = c(0.12,0)) +
    labs(x = NULL, y = "Years to recover") +
    # rectangle with gradient
    theme(legend.position = "none", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8), strip.background = element_blank(),strip.placement = "outside") +
    #scale_colour_gradient(low = "#290934", high = "#C6B9CA")
    scale_color_gradientn(colors = c("#290934", "#84678D", "#C6B9CA"), limits = c(min(param_yr_df1$recover, na.rm = T), max(param_yr_df1$recover, na.rm = T))) #+
   # coord_cartesian(clip = "off") +
   # annotation_custom(grid::rectGrob(x = unit(0.008, "npc"), y = unit(0.5, "npc"),
   #                                   width = unit(1, "mm"), height = unit(25, "mm"), gp = gpar(col = NA, fill = grid::linearGradient(colour = c("#f29414", "#f3f59e", "#4D8F26"), stops = c(0, 0.5, 1)), lwd = unit(0.1, "pt"))))

jpeg("~/code availability/outputs/param_percent_yr.jpg", height = 17, width = 16, units = "cm", res = 600)  ###PATH NAME###
p_plot_yr %>%  annotate_figure(left = grid::rectGrob(x = unit(0.008, "npc"), y = unit(0.5, "npc"), width = unit(1, "mm"), height = unit(32, "mm"), gp = gpar(col = NA, fill = grid::linearGradient(colour = c("#290934", "#84678D", "#C6B9CA"), stops = c(0, 0.5, 1)), lwd = unit(0.1, "pt")), hjust = -17, vjust = 0.18)) %>%  
  annotate_figure(left = grid::rectGrob(x = unit(0.008, "npc"), y = unit(0.5, "npc"), width = unit(1, "mm"), height = unit(32, "mm"), gp = gpar(col = NA, fill = grid::linearGradient(colour = c("#290934", "#84678D", "#C6B9CA"), stops = c(0, 0.5, 1)), lwd = unit(0.1, "pt")), hjust = -20.55, vjust = -1.58)) %>% 
   annotate_figure(left = grid::rectGrob(x = unit(0.008, "npc"), y = unit(0.5, "npc"), width = unit(1, "mm"), height = unit(32, "mm"), gp = gpar(col = NA, fill = grid::linearGradient(colour = c("#290934", "#84678D", "#C6B9CA"), stops = c(0, 0.5, 1)), lwd = unit(0.1, "pt")), hjust = -24, vjust = 1.95))

```

## change across ranges
```{r}
rec_diff <- lapply(param_mean_dfs, function(x) x$mean[[11]] - x$mean[[1]])

yr_diff <- lapply(param_yr_mean_dfs, function(x) x$mean[[11]] - x$mean[[1]])
```


## X times initial amount
```{r}
p_times_rec <- lapply(param_mean_dfs, funciton(x) {
  ifelse(x[[11,2]]>x[[1,2]], x[[11,2]]/x[[1,2]], x[[1,2]] /x[[11,2]])# function depends on if parameter causes increase or decrease in response
})


p_times_yr <- lapply(param_yr_mean_dfs, funciton(x) {
  ifelse(x[[11,2]]>x[[1,2]], x[[11,2]]/x[[1,2]], x[[1,2]] /x[[11,2]]) 
})
```

