---
title: "C lm aboveground"
author: "Emmerson Wilson"
date: "2024-01-18"
output:
 pdf_document:
   toc: true
   toc_depth: 5
classoption: landscape
---

```{r}
pacman::p_load(
  dplyr,
  tidyverse,
  readxl,
  cv,
  lme4,
  boot,
  MuMIn,
  sjPlot,
  AICcmodavg)
  
```

# data

# c at sites

```{r}
library(httr)

github_link_blw1 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/c_m2_site_below.xlsx?raw=true"

temp_file_blw1 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req_blw1 <- GET(github_link_blw1, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file_blw1))
c_m2_sites_blw <- read_xlsx(temp_file_blw1)%>% 
  rename(unique_id = "id")
c_m2_sites_blw
```

# c at subplots

```{r}
github_link_blw2 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/c_m2_subplot_below.xlsx?raw=true"

temp_file_blw2 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req_blw2 <- GET(github_link_blw2, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file_blw2))
c_m2_subplots_blw <- read_xlsx(temp_file_blw2)  
c_m2_subplots_blw
```

# environmental variables at sites

```{r}
github_link3 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/env_site_final.xlsx?raw=true"

temp_file3 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req3 <- GET(github_link3, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file3))
env_site_final <- read_xlsx(temp_file3)
env_site_final

c_blw_env_sites <- full_join(c_m2_sites_blw, env_site_final) %>%
  dplyr::select(!c(FAC, CC, CEC_LCT, dominant))
c_blw_env_sites$Moose_new <- as.character(c_blw_env_sites$Moose_new)

  
#subset by park
c_blw_env_sites_GM <- c_blw_env_sites %>% 
  filter(park == "GM") 

c_blw_env_sites_TN <- c_blw_env_sites %>% 
  filter(park == "TN") 

#scale predictor variables (but don't center around 0)
c_blw_env_sites_scale <- c_blw_env_sites

c_blw_env_sites_scale[c(11:16, 18)] <- scale(c_blw_env_sites_scale[c(11:16, 18)], center = F)

c_blw_env_sites_scale_GM <- c_blw_env_sites_scale %>% 
  filter(park == "GM")

c_blw_env_sites_scale_GM["Moose_new"][c_blw_env_sites_scale_GM["Moose_new"] == 1] <- "aL"
c_blw_env_sites_scale_GM["Moose_new"][c_blw_env_sites_scale_GM["Moose_new"] == 2] <- "aL"
c_blw_env_sites_scale_GM["Moose_new"][c_blw_env_sites_scale_GM["Moose_new"] == 3] <- "bH"
c_blw_env_sites_scale_GM["Moose_new"][c_blw_env_sites_scale_GM["Moose_new"] == 4] <- "cX"

c_blw_env_sites_scale_TN <- c_blw_env_sites_scale %>% 
  filter(park == "TN")

c_blw_env_sites_scale_TN["Moose_new"][c_blw_env_sites_scale_TN["Moose_new"] == 1] <- "aL"
c_blw_env_sites_scale_TN["Moose_new"][c_blw_env_sites_scale_TN["Moose_new"] == 2] <- "bM"
c_blw_env_sites_scale_TN["Moose_new"][c_blw_env_sites_scale_TN["Moose_new"] == 3] <- "cH"
c_blw_env_sites_scale_TN["Moose_new"][c_blw_env_sites_scale_TN["Moose_new"] == 4] <- "dV"


```

# environmental variables at each subplot

```{r}
github_link4 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/env_subplots_final.xlsx?raw=true"

temp_file4 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req4 <- GET(github_link4, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file4))
env_subplot_final <- read_xlsx(temp_file4)
env_subplot_final

c_blw_env_subplots <- full_join(c_m2_subplots_blw, env_subplot_final) %>%
  dplyr::select(!c(FAC, CC, CEC_LCT, SPC))
c_blw_env_subplots$Moose_new <- as.character(c_blw_env_subplots$Moose_new)  

#subset by park
c_blw_env_subplots_GM <- c_blw_env_subplots %>% 
  filter(park_id == "GM")


c_blw_env_subplots_TN <- c_blw_env_subplots %>% 
  filter(park_id == "TN")


# scale environmental variables (but don't center around 0)

c_blw_env_sub_scale <- c_blw_env_subplots

c_blw_env_sub_scale[c(21:26, 28)] <- scale(c_blw_env_sub_scale[c(21:26, 28)], center = F)

c_blw_env_sub_scale_GM <- c_blw_env_sub_scale %>% 
  filter(park_id == "GM")

c_blw_env_sub_scale_GM["Moose_new"][c_blw_env_sub_scale_GM["Moose_new"] == 1] <- "aL"
c_blw_env_sub_scale_GM["Moose_new"][c_blw_env_sub_scale_GM["Moose_new"] == 2] <- "aL"
c_blw_env_sub_scale_GM["Moose_new"][c_blw_env_sub_scale_GM["Moose_new"] == 3] <- "bH"
c_blw_env_sub_scale_GM["Moose_new"][c_blw_env_sub_scale_GM["Moose_new"] == 4] <- "cX"


c_blw_env_sub_scale_TN <- c_blw_env_sub_scale %>% 
  filter(park_id == "TN") 

c_blw_env_sub_scale_TN["Moose_new"][c_blw_env_sub_scale_TN["Moose_new"] == 1] <- "aL"
c_blw_env_sub_scale_TN["Moose_new"][c_blw_env_sub_scale_TN["Moose_new"] == 2] <- "bM"
c_blw_env_sub_scale_TN["Moose_new"][c_blw_env_sub_scale_TN["Moose_new"] == 3] <- "cH"
c_blw_env_sub_scale_TN["Moose_new"][c_blw_env_sub_scale_TN["Moose_new"] == 4] <- "dV"

```

# model functions

```{r}
source("https://github.com/emmwilson/C_forecasting_NL/blob/main/code_for_stats/lmer%20model%20functions.R?raw=true")

R2 <- function(model){
  with(summary(model), 1 - deviance/null.deviance)
}
```


# GM


## by site

### null

```{r}
#run the model
GM_blw_lm_null <- lm_glm(c_blw_env_sites_scale_GM, "c_m2_site_blw", "1")

# get the summary of the model into a dataframe
GM_blw_lm_null_summary <- as.data.frame(summary(GM_blw_lm_null)$coefficients) %>% 
  mutate(model = "GM_blw_lm_null") 
GM_blw_lm_null_summary <- GM_blw_lm_null_summary %>% 
  add_column("predictor" = rownames(GM_blw_lm_null_summary))

# reorder columns so model name first
GM_blw_lm_null_summary <- GM_blw_lm_null_summary[,c(5,6,1:4)]

```

### full

```{r}
# make list of all variables to be included in full model
full_var <- list("FHT", "EVIamp", "EVImed", "ELE", "SLO", "ASP", "LGS", "Moose_new")

# run the model
GM_blw_lm_full <- lm_glm(c_blw_env_sites_scale_GM, "c_m2_site_blw", full_var)

# thoughts: FHT obviously important. seems no effect of moose levels - want to see if moose are correlated with forest height

# add summary of model to dataframe
GM_blw_lm_full_summary <- as.data.frame(summary(GM_blw_lm_full)$coefficients) %>% 
  mutate(model = "GM_blw_lm_full") 
GM_blw_lm_full_summary <- GM_blw_lm_full_summary %>% 
  add_column("predictor" = rownames(GM_blw_lm_full_summary))

GM_blw_lm_full_summary <- GM_blw_lm_full_summary[,c(5,6,1:4)]
GM_blw_lm_full_summary
```


### univariate

```{r}
# run model with each predictor variable on own

GM_blw_lm_uni <- lapply(full_var, lm_glm, df = c_blw_env_sites_scale_GM, c = "c_m2_site_blw")


names(GM_blw_lm_uni) <- full_var # make sure names of objects in list consistent

GM_blw_lm_uni_summary <- lapply(GM_blw_lm_uni, summary)

GM_blw_lm_uni_summary

#thoughts: FHT obviosuly important again. strange that full model had EVImed as sig but univariate has EVIamp as sig (will try diff combos of reduced to explore). 

```

## summary of uni, null and full

```{r}
# get summary of each univariate model, add them to a single dataframe with model name and variables in own columns


GM_blw_uni_summary_all <- Reduce(full_join,lapply(mapply(cbind, lapply(lapply(GM_blw_lm_uni_summary, coef), as.data.frame), "model"=names(GM_blw_lm_uni_summary), SIMPLIFY=F), rownames_to_column, var = "predictor")) 
GM_blw_uni_summary_all <- GM_blw_uni_summary_all[,c(5,6,1:4)]
GM_blw_uni_summary_all

# combine summary dataframes for null, full and univariate models
GM_blw_lm_summary <- rbind(GM_blw_lm_null_summary, GM_blw_lm_full_summary, GM_blw_uni_summary_all) 
GM_blw_lm_summary <- GM_blw_lm_summary %>% 
  mutate(significance = ifelse(GM_blw_lm_summary$`Pr(>|t|)` < 0.001, "***", ifelse(GM_blw_lm_summary$`Pr(>|t|)` < 0.01, "**", ifelse(GM_blw_lm_summary$`Pr(>|t|)` < 0.05, "*", ifelse(GM_blw_lm_summary$`Pr(>|t|)` < 0.1, ".", " "))))) # add symbols for easy visualization of sigificance
```

thoughts: not much to unravel here. nothig explains the variance in below ground carbon well. I could get some soil characteristic rasters, but at a 250 m scale. The Sothe et al 2022 paper that predicted below ground carbon said soil depth was the main explanatory variable for below ground carbon. It also seemed that envionmental variables played a role in predicting below ground (max daily temp, daily precip and solar radiation). Enviornmental data I could only get at 1km resolution. The sothe et al paper did use 1 km rasters and downsampled to 250m.

## compare

```{r}
# see excel "c_lm_model_results.xlsx" for consolidated values

# add univariate, null and full models into a list
GM_blw_models_r <- list()

GM_blw_models_r[["GM_blw_lm_null"]] <- GM_blw_lm_null
GM_blw_models_r[["GM_blw_lm_full"]] <- GM_blw_lm_full
GM_blw_models_r[[names(GM_blw_lm_uni)[1]]] <- GM_blw_lm_uni[[1]]
GM_blw_models_r[[names(GM_blw_lm_uni)[2]]] <- GM_blw_lm_uni[[2]]
GM_blw_models_r[[names(GM_blw_lm_uni)[3]]] <- GM_blw_lm_uni[[3]]
GM_blw_models_r[[names(GM_blw_lm_uni)[4]]] <- GM_blw_lm_uni[[4]]
GM_blw_models_r[[names(GM_blw_lm_uni)[5]]] <- GM_blw_lm_uni[[5]]
GM_blw_models_r[[names(GM_blw_lm_uni)[6]]] <- GM_blw_lm_uni[[6]]
GM_blw_models_r[[names(GM_blw_lm_uni)[7]]] <- GM_blw_lm_uni[[7]]
GM_blw_models_r[[names(GM_blw_lm_uni)[8]]] <- GM_blw_lm_uni[[8]]

Modnames_GM_blw_r <- paste(names(GM_blw_models_r)) # make sure names are same as model name

# get table
aic_GM_blw <- as.data.frame(aictab(cand.set = GM_blw_models_r, modnames = Modnames_GM_blw_r, sort = TRUE))
  
R2_GM_blw <- as.data.frame(sapply(GM_blw_models_r, R2)) %>% setNames(c("R2"))
R2_GM_blw <- R2_GM_blw %>%
  mutate("Modnames" = rownames(R2_GM_blw))

aic_R2_GM_blw <- full_join(aic_GM_blw, R2_GM_blw)
  
```

### reduced





## by subplot

### null

```{r}
# fixed effects - very much pseaudoreplication but ran the models out of curiosity
GM_blw_lm_null_subfe <- lm_glm(c_blw_env_sub_scale_GM, "c_m2_subplot_blw", "1")

summary(GM_blw_lm_null_subfe)

# mixed effects
GM_blw_lm_null_sub <- lm_lmer(c_blw_env_sub_scale_GM, "c_m2_subplot_blw", "1")

GM_blw_lm_null_sub_summary <- summary(GM_blw_lm_null_sub)
r.squaredGLMM(GM_blw_lm_null_sub)
```

### full

```{r}
# fixed effects

GM_blw_lm_full_subfe <- lm_glm(c_blw_env_sub_scale_GM, "c_m2_subplot_blw", full_var)

# mixed effects
GM_blw_lm_full_sub <- lm_lmer(c_blw_env_sub_scale_GM, "c_m2_subplot_blw", full_var)
```

### univariate

```{r}
# fixed effects

GM_blw_lm_uni_subfe <- lapply(full_var, lm_glm, df = c_blw_env_sub_scale_GM, c = "c_m2_subplot_blw")

names(GM_blw_lm_uni_subfe) <- full_var

GM_blw_lm_uni_subfe_summary <- lapply(GM_blw_lm_uni_subfe, summary)

# mixed effects

GM_blw_lm_uni_sub <- lapply(full_var, lm_lmer, df = c_blw_env_sub_scale_GM, c = "c_m2_subplot_blw")

names(GM_blw_lm_uni_sub) <- full_var

GM_blw_lm_uni_sub_summary <- lapply(GM_blw_lm_uni_sub, summary)

GM_blw_lm_uni_sub_r2 <- lapply(GM_blw_lm_uni_sub, r.squaredGLMM)

```

## compare

```{r}
GM_blw_models_subfe_r <- list()

GM_blw_models_subfe_r[["GM_blw_lm_null_subfe"]] <- GM_blw_lm_null_subfe
GM_blw_models_subfe_r[["GM_blw_lm_full_subfe"]] <- GM_blw_lm_full_subfe
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[1]]] <- GM_blw_lm_uni_subfe[[1]]
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[2]]] <- GM_blw_lm_uni_subfe[[2]]
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[3]]] <- GM_blw_lm_uni_subfe[[3]]
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[4]]] <- GM_blw_lm_uni_subfe[[4]]
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[5]]] <- GM_blw_lm_uni_subfe[[5]]
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[6]]] <- GM_blw_lm_uni_subfe[[6]]
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[7]]] <- GM_blw_lm_uni_subfe[[7]]
GM_blw_models_subfe_r[[names(GM_blw_lm_uni_subfe)[8]]] <- GM_blw_lm_uni_subfe[[8]]

Modnames_GM_blw_subfe_r <- paste(names(GM_blw_models_subfe_r))

# get table
aic_GM_blw_sub_fe <- aictab(cand.set = GM_blw_models_subfe_r, modnames = Modnames_GM_blw_subfe_r, sort = TRUE)

#mixed effect
GM_blw_models_sub_r <- list()

GM_blw_models_sub_r[["GM_blw_lm_null_sub"]] <- GM_blw_lm_null_sub
GM_blw_models_sub_r[["GM_blw_lm_full_sub"]] <- GM_blw_lm_full_sub
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[1]]] <- GM_blw_lm_uni_sub[[1]]
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[2]]] <- GM_blw_lm_uni_sub[[2]]
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[3]]] <- GM_blw_lm_uni_sub[[3]]
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[4]]] <- GM_blw_lm_uni_sub[[4]]
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[5]]] <- GM_blw_lm_uni_sub[[5]]
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[6]]] <- GM_blw_lm_uni_sub[[6]]
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[7]]] <- GM_blw_lm_uni_sub[[7]]
GM_blw_models_sub_r[[names(GM_blw_lm_uni_sub)[8]]] <- GM_blw_lm_uni_sub[[8]]

Modnames_GM_blw_sub_r <- paste(names(GM_blw_models_sub_r))

# get table
 aic_GM_blw_sub <- aictab(cand.set = GM_blw_models_sub_r, modnames = Modnames_GM_blw_sub_r, sort = TRUE) 

R2_GM_blw_sub <- as.data.frame(sapply(GM_blw_models_sub_r, r.squaredGLMM)) %>% t() %>%  as.data.frame() %>% setNames(c("R2m", "R2c"))
R2_GM_blw_sub <- R2_GM_blw_sub %>% 
   mutate("Modnames" = rownames(R2_GM_blw_sub))

aic_R2_GM_blw_sub <- full_join(aic_GM_blw_sub, R2_GM_blw_sub)
 
 
view(aic_R2_GM_blw_sub)
```

thoughts: apparently there is huge amounts of random variation between sites. adding a random effect of site shoots the R2c up to alost 80%

### reduced


# TN

## temporarily setTN 05


```{r}
c_blw_env_sites_scale_TN$Moose_new <-replace_na(c_blw_env_sites_scale_TN$Moose_new, "cH")

c_blw_env_sub_scale_TN$Moose_new <-replace_na(c_blw_env_sub_scale_TN$Moose_new, "cH")
```


## by site

### null

```{r}
#run the model
TN_blw_lm_null <- lm_glm(c_blw_env_sites_scale_TN, "c_m2_site_blw", "1")

# get the summary of the model into a dataframe
TN_blw_lm_null_summary <- as.data.frame(summary(TN_blw_lm_null)$coefficients) %>% 
  mutate(model = "TN_blw_lm_null") 
TN_blw_lm_null_summary <- TN_blw_lm_null_summary %>% 
  add_column("predictor" = rownames(TN_blw_lm_null_summary))

# reorder columns so model name first
TN_blw_lm_null_summary <- TN_blw_lm_null_summary[,c(5,6,1:4)]
TN_blw_lm_null_summary
```

### full

```{r}
# make list of all variables to be included in full model
full_var <- list("FHT", "EVIamp", "EVImed", "ELE", "SLO", "ASP", "LGS", "Moose_new")

# run the model
TN_blw_lm_full <- lm_glm(c_blw_env_sites_scale_TN, "c_m2_site_blw", full_var)

# thoughts: FHT obviously important. seems no effect of moose levels - want to see if moose are correlated with forest height

# add summary of model to dataframe
TN_blw_lm_full_summary <- as.data.frame(summary(TN_blw_lm_full)$coefficients) %>% 
  mutate(model = "TN_blw_lm_full") 
TN_blw_lm_full_summary <- TN_blw_lm_full_summary %>% 
  add_column("predictor" = rownames(TN_blw_lm_full_summary))

TN_blw_lm_full_summary <- TN_blw_lm_full_summary[,c(5,6,1:4)]
TN_blw_lm_full_summary
```


### univariate

```{r}
# run model with each predictor variable on own

TN_blw_lm_uni <- lapply(full_var, lm_glm, df = c_blw_env_sites_scale_TN, c = "c_m2_site_blw")


names(TN_blw_lm_uni) <- full_var # make sure names of objects in list consistent

TN_blw_lm_uni_summary <- lapply(TN_blw_lm_uni, summary)

TN_blw_lm_uni_summary

#thoughts: FHT obviosuly important again. strange that full model had EVImed as sig but univariate has EVIamp as sig (will try diff combos of reduced to explore). 

```

## summary of uni, null and full

```{r}
# get summary of each univariate model, add them to a single dataframe with model name and variables in own columns


TN_blw_uni_summary_all <- Reduce(full_join,lapply(mapply(cbind, lapply(lapply(TN_blw_lm_uni_summary, coef), as.data.frame), "model"=names(TN_blw_lm_uni_summary), SIMPLIFY=F), rownames_to_column, var = "predictor")) 
TN_blw_uni_summary_all <- TN_blw_uni_summary_all[,c(5,6,1:4)]
TN_blw_uni_summary_all

# combine summary dataframes for null, full and univariate models
TN_blw_lm_summary <- rbind(TN_blw_lm_null_summary, TN_blw_lm_full_summary, TN_blw_uni_summary_all) 
TN_blw_lm_summary <- TN_blw_lm_summary %>% 
  mutate(significance = ifelse(TN_blw_lm_summary$`Pr(>|t|)` < 0.001, "***", ifelse(TN_blw_lm_summary$`Pr(>|t|)` < 0.01, "**", ifelse(TN_blw_lm_summary$`Pr(>|t|)` < 0.05, "*", ifelse(TN_blw_lm_summary$`Pr(>|t|)` < 0.1, ".", " "))))) # add symbols for easy visualization of sigificance
```

## compare

```{r}
# see excel "c_lm_model_results.xlsx" for consolidated values

# add univariate, null and full models into a list
TN_blw_models_r <- list()

TN_blw_models_r[["TN_blw_lm_null"]] <- TN_blw_lm_null
TN_blw_models_r[["TN_blw_lm_full"]] <- TN_blw_lm_full
TN_blw_models_r[[names(TN_blw_lm_uni)[1]]] <- TN_blw_lm_uni[[1]]
TN_blw_models_r[[names(TN_blw_lm_uni)[2]]] <- TN_blw_lm_uni[[2]]
TN_blw_models_r[[names(TN_blw_lm_uni)[3]]] <- TN_blw_lm_uni[[3]]
TN_blw_models_r[[names(TN_blw_lm_uni)[4]]] <- TN_blw_lm_uni[[4]]
TN_blw_models_r[[names(TN_blw_lm_uni)[5]]] <- TN_blw_lm_uni[[5]]
TN_blw_models_r[[names(TN_blw_lm_uni)[6]]] <- TN_blw_lm_uni[[6]]
TN_blw_models_r[[names(TN_blw_lm_uni)[7]]] <- TN_blw_lm_uni[[7]]
TN_blw_models_r[[names(TN_blw_lm_uni)[8]]] <- TN_blw_lm_uni[[8]]

Modnames_TN_blw_r <- paste(names(TN_blw_models_r)) # make sure names are same as model name

# get table
aic_TN_blw <- as.data.frame(aictab(cand.set = TN_blw_models_r, modnames = Modnames_TN_blw_r, sort = TRUE))
  
R2_TN_blw <- as.data.frame(sapply(TN_blw_models_r, R2)) %>% setNames(c("R2"))
R2_TN_blw <- R2_TN_blw %>%
  mutate("Modnames" = rownames(R2_TN_blw))

aic_R2_TN_blw <- full_join(aic_TN_blw, R2_TN_blw)
```

thoughts: still not much variance explained by predictor variables

### reduced




## by subplot

### null

```{r}
# fixed effects - very much pseaudoreplication but ran the models out of curiosity
TN_blw_lm_null_subfe <- lm_glm(c_blw_env_sub_scale_TN, "c_m2_subplot_blw", "1")

# mixed effects
TN_blw_lm_null_sub <- lm_lmer(c_blw_env_sub_scale_TN, "c_m2_subplot_blw", "1")

TN_blw_lm_null_sub_summary <- summary(TN_blw_lm_null_sub)
r.squaredGLMM(TN_blw_lm_null_sub)
```

### full

```{r}
# fixed effects

TN_blw_lm_full_subfe <- lm_glm(c_blw_env_sub_scale_TN, "c_m2_subplot_blw", full_var)

# mixed effects
TN_blw_lm_full_sub <- lm_lmer(c_blw_env_sub_scale_TN, "c_m2_subplot_blw", full_var)

summary(TN_blw_lm_full_sub)
r.squaredGLMM(TN_blw_lm_full_sub)
```

### univariate

```{r}
# fixed effects

TN_blw_lm_uni_subfe <- lapply(full_var, lm_glm, df = c_blw_env_sub_scale_TN, c = "c_m2_subplot_blw")

names(TN_blw_lm_uni_subfe) <- full_var

TN_blw_lm_uni_subfe_summary <- lapply(TN_blw_lm_uni_subfe, summary)

# mixed effects

TN_blw_lm_uni_sub <- lapply(full_var, lm_lmer, df = c_blw_env_sub_scale_TN, c = "c_m2_subplot_blw")

names(TN_blw_lm_uni_sub) <- full_var

TN_blw_lm_uni_sub_summary <- lapply(TN_blw_lm_uni_sub, summary)

TN_blw_lm_uni_sub_r2 <- lapply(TN_blw_lm_uni_sub, r.squaredGLMM)
```

## compare

```{r}
TN_blw_models_subfe_r <- list()

TN_blw_models_subfe_r[["TN_blw_lm_null_subfe"]] <- TN_blw_lm_null_subfe
TN_blw_models_subfe_r[["TN_blw_lm_full_subfe"]] <- TN_blw_lm_full_subfe
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[1]]] <- TN_blw_lm_uni_subfe[[1]]
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[2]]] <- TN_blw_lm_uni_subfe[[2]]
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[3]]] <- TN_blw_lm_uni_subfe[[3]]
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[4]]] <- TN_blw_lm_uni_subfe[[4]]
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[5]]] <- TN_blw_lm_uni_subfe[[5]]
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[6]]] <- TN_blw_lm_uni_subfe[[6]]
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[7]]] <- TN_blw_lm_uni_subfe[[7]]
TN_blw_models_subfe_r[[names(TN_blw_lm_uni_subfe)[8]]] <- TN_blw_lm_uni_subfe[[8]]

Modnames_TN_blw_subfe_r <- paste(names(TN_blw_models_subfe_r))

# get table
aic_TN_blw_sub_fe <- aictab(cand.set = TN_blw_models_subfe_r, modnames = Modnames_TN_blw_subfe_r, sort = TRUE) 


TN_blw_models_sub_r <- list()

TN_blw_models_sub_r[["TN_blw_lm_null_sub"]] <- TN_blw_lm_null_sub
TN_blw_models_sub_r[["TN_blw_lm_full_sub"]] <- TN_blw_lm_full_sub
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[1]]] <- TN_blw_lm_uni_sub[[1]]
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[2]]] <- TN_blw_lm_uni_sub[[2]]
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[3]]] <- TN_blw_lm_uni_sub[[3]]
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[4]]] <- TN_blw_lm_uni_sub[[4]]
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[5]]] <- TN_blw_lm_uni_sub[[5]]
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[6]]] <- TN_blw_lm_uni_sub[[6]]
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[7]]] <- TN_blw_lm_uni_sub[[7]]
TN_blw_models_sub_r[[names(TN_blw_lm_uni_sub)[8]]] <- TN_blw_lm_uni_sub[[8]]

Modnames_TN_blw_sub_r <- paste(names(TN_blw_models_sub_r))

# get table
# get table
 aic_TN_blw_sub <- aictab(cand.set = TN_blw_models_sub_r, modnames = Modnames_TN_blw_sub_r, sort = TRUE) 

R2_TN_blw_sub <- as.data.frame(sapply(TN_blw_models_sub_r, r.squaredGLMM)) %>% t() %>%  as.data.frame() %>% setNames(c("R2m", "R2c"))
R2_TN_blw_sub <- R2_TN_blw_sub %>% 
   mutate("Modnames" = rownames(R2_TN_blw_sub))

aic_R2_TN_blw_sub <- full_join(aic_TN_blw_sub, R2_TN_blw_sub)

aic_R2_TN_blw_sub
```

thoughts: again adding random effect of site shoots the R2c to alomst 0.8

### reduced


