---
title: "C_explore_22_23"
format: html
editor: visual
---

```{r}
pacman::p_load(
  tidyverse,
  readxl,
  ggplot2,
  janitor,
  vegan,
  stringr,
  reshape2)
```

## prep c data sets for combining

### 2022 data

```{r}
#combine individual excel files fror carbon in each pool
c_2022_dw <- read_xlsx("../final carbon data/Final_Carbon_Data_R/Rachael 2022 measurements/Deadwood_Field_Data NEW.xlsm", sheet = "DW carbon") %>%
  dplyr::select(c(Site_Subplot_ID, dw_carbon_9m2))
c_2022_te <- read_xlsx("../final carbon data/Final_Carbon_Data_R/Rachael 2022 measurements/Tree_Biomass_NEW.xlsm", sheet = "Tree carbon") %>%
  dplyr::select(c(Site_Subplot_ID, te_carbon_9m2))
c_2022_gc <- read_xlsx("../final carbon data/Final_Carbon_Data_R/ground_cover_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, gc_carbon_9m2))
c_2022_hb <- read_xlsx("../final carbon data/Final_Carbon_Data_R/herbaceous_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, hb_carbon_9m2))
c_2022_ll <- read_xlsx("../final carbon data/Final_Carbon_Data_R/litter_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Park_ID, Site_ID, Ex_Ctrl, Subplot_ID, Site_Subplot_ID, ll_carbon_9m2))
c_2022_sp <- read_xlsx("../final carbon data/Final_Carbon_Data_R/sapling_carbon.xlsx", sheet = "Sheet 1") %>% dplyr::select(c(Site_Subplot_ID, sp_carbon_9m2))
#c_2022_sr <- read_xlsx("Final_Carbon_Data_R/shrub_root_carbon.xlsx", sheet = "Sheet 1") because this data came before R fixed the under 30 units I need to calculate on my own
c_2022_sl <- read_xlsx("../final carbon data/Final_Carbon_Data_R/soil_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, sl_carbon_9m2))

c_2022_tr <- read_xlsx("../final carbon data/Final_Carbon_Data_R/Rachael 2022 measurements/Tree_Biomass_NEW.xlsm", sheet = "Tree root carbon") %>%
  dplyr::select(c(Site_Subplot_ID, tr_carbon_9m2))
c_2022_u3 <- read_xlsx("../final carbon data/Final_Carbon_Data_R/under_30_carbon.xlsx", sheet = "Sheet 1") %>%
  mutate(u3_carbon_9m2 = u3_carbon_9m2/1000000) %>% # convert units
  dplyr::select(c(Site_Subplot_ID, u3_carbon_9m2))
c_2022_ws <- read_xlsx("../final carbon data/Final_Carbon_Data_R/woody_shrubs_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, ws_carbon_9m2))
site_data_2022 <- read_xlsx("../final carbon data/Final_Carbon_Data_R/subplot_disturbacne.xlsx")

c_2022_sr_list <- list(c_2022_u3, c_2022_ws, c_2022_sp)
c_2022_sr <- c_2022_sr_list %>% reduce(full_join, by='Site_Subplot_ID') %>%
  replace(is.na(.), 0)
c_2022_sr$sr_carbon_9m2 <- rowSums(c_2022_sr[, c(2:4)])
c_2022_sr <- c_2022_sr %>% dplyr::select(c(1,5)) %>%
  mutate(sr_carbon_9m2 = sr_carbon_9m2*0.25)
  

c_2022_list <- list(c_2022_dw, c_2022_te, c_2022_gc, c_2022_hb, c_2022_ll, c_2022_sp, c_2022_sr, c_2022_sl, c_2022_tr, c_2022_u3, c_2022_ws)

c_2022 <- c_2022_list %>% reduce(full_join, by='Site_Subplot_ID') %>%
  dplyr::select(c(1,6:9,2:5,10:16)) %>%
  replace(is.na(.), 0)
c_2022$total_c_per_subplot <- rowSums(c_2022[, c(6:16)])

c_2022_mess <- c_2022 %>%
  left_join(site_data_2022) %>% # add subplot info
  clean_names() %>%
  mutate(gap = disturbance) %>% 
  mutate(across('gap', str_replace, 'Insect', 'Gap')) %>% # add if gap or not gap
  mutate(across('gap', str_replace, 'Fire', 'Gap')) %>%
  mutate(ss_carbon_9m2 = rowSums(c_2022[, c("sp_carbon_9m2", "ws_carbon_9m2")])) %>% # recategorize pools to match 2023
  mutate(rt_carbon_9m2 = rowSums(c_2022[, c("tr_carbon_9m2","sr_carbon_9m2")])) %>%
  mutate(gv_carbon_9m2 = rowSums(c_2022[, c("gc_carbon_9m2", "hb_carbon_9m2", "u3_carbon_9m2")])) %>%
  mutate(year = 2022) %>% # add year
  mutate(site_number = as.numeric(site_id))
c_2022_mess$site_number <- sprintf("%02.f", c_2022_mess$site_number)
c_2022_mess <- c_2022_mess %>%
  mutate(site_id = paste0(site_number, "_", "2022")) %>% # distinguish overlapping site numbers by year
  mutate(subplot_id = substr(subplot_id,2,2)) %>% # remove letter from subplot
  filter(ex_ctrl != "EX")

c_2022_compat <- c_2022_mess %>%
  dplyr::select(c(2:5,18,19,23,6,7,10,13,20:22,17))
```

![](data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAcElEQVR4Xu3OwQmAQAxE0bClWYCW5N06tM6V2YPg5CjoF/JhLoHAi6iqn9eOefUbqrYvHY0cQDLyAlKRNyARmYA0ZMLRkAlGQyaU72tkAtlim7r/vJqDUDjlKBROOQyFU2icQuMUGqfQuBEaV1XPOwEx96nYACK8+wAAAABJRU5ErkJggg== "Run Current Chunk")

### 2023 data

```{r results='hide', message=FALSE}
c_2023 <- read_xlsx("../final carbon data/carbon_data_2023.xlsm", sheet = "Overall C") %>%
  replace(is.na(.), 0) 

site_data <- read_xlsx("../final carbon data/carbon_data_2023.xlsm", sheet = "Subplot info")
site_data$Site_ID <- sprintf("%02.f", site_data$Site_ID)

c_2023_mess <- c_2023 %>%
  left_join(site_data)%>%
  clean_names() %>%
  mutate(gap = disturbance) %>%
  mutate(across('gap', str_replace, 'Insect', 'Gap')) %>% # add if gap or not gap
  mutate(across('gap', str_replace, 'Fire', 'Gap')) %>%
  mutate(across('gap', str_replace, 'Wind', 'Gap')) %>%
  mutate(across('gap', str_replace, 'Logging', 'Gap')) %>%
  mutate(year = 2023) %>% # add year
  mutate(site_id = paste0(site_id, "_", "2023")) %>% # distinguish overlapping site numbers by year
  filter(ex_ctrl != "EX") 
  

c_2023_compat <- c_2023_mess %>%
  dplyr::select(c(22,23,25,2,27,38,39,5,7,10,11,13,16,18,21)) %>%
  replace(is.na(.), 0)
```

### combine 2022&2023

```{r}
c_22_23 <- rbind(c_2022_compat, c_2023_compat) %>%
  mutate(unique_id = paste0(park_id, "_", site_id, "_", subplot_id))

# compare total C bw years
summary(c_2022_compat$total_c_per_subplot)[[4]]
summary(c_2023_compat$total_c_per_subplot)[[4]]
sum(c_2022_compat$total_c_per_subplot)
sum(c_2023_compat$total_c_per_subplot)

ggplot(c_22_23, aes(x=factor(year), y=total_c_per_subplot, fill = park_id)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               aes(colour = park_id))


ggplot(c_22_23, aes(x=factor(year), y=total_c_per_subplot, colour = interaction(gap, park_id, sep=':'))) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               aes(colour = interaction(gap, park_id, sep=':'))) + theme(legend.title = element_blank())


ggplot(c_22_23, aes(x=factor(year), y=total_c_per_subplot)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")


ggplot(c_22_23, aes(x=factor(gap), y=total_c_per_subplot)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")


ggplot(c_22_23, aes(x=factor(park_id), y=total_c_per_subplot, colour = gap)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               aes(colour = gap))

```

```{r}
# compare tree C bw years
summary(c_2022_compat$te_carbon_9m2)
summary(c_2023_compat$te_carbon_9m2)

v_NL_te <- ggplot(c_22_23, aes(x= factor(year), y=te_carbon_9m2)) + 
  geom_violin()
v_NL_te

v_NL_te_yr_gap <- ggplot(c_22_23, aes(x=factor(year), y=te_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())
v_NL_te_yr_gap

# compare shrub and sapling C bw years
summary(c_2022_compat$ss_carbon_9m2)
summary(c_2023_compat$ss_carbon_9m2)

v_NL_ss <- ggplot(c_22_23, aes(x=factor(year), y=ss_carbon_9m2)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")
v_NL_ss

v_NL_ss_yr_gap <- ggplot(c_22_23, aes(x=factor(year), y=ss_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())
v_NL_ss_yr_gap

# compare root C bw years
summary(c_2022_compat$rt_carbon_9m2)
summary(c_2023_compat$rt_carbon_9m2)

v_NL_rt <- ggplot(c_22_23, aes(x=factor(year), y=rt_carbon_9m2)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")
v_NL_rt

v_NL_rt_yr_gap <- ggplot(c_22_23, aes(x=factor(year), y=rt_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())
v_NL_rt_yr_gap

# compare deadwood C bw years
summary(c_2022_compat$dw_carbon_9m2)
summary(c_2023_compat$dw_carbon_9m2)

v_NL_dw <- ggplot(c_22_23, aes(x=factor(year), y=dw_carbon_9m2)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")
v_NL_dw

v_NL_dw_yr_gap <- ggplot(c_22_23, aes(x=factor(year), y=dw_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())
v_NL_dw_yr_gap

# compare ground veg C bw years
summary(c_2022_compat$gv_carbon_9m2)
summary(c_2023_compat$gv_carbon_9m2)

v_NL_gv <- ggplot(c_22_23, aes(x=factor(year), y=gv_carbon_9m2)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")
v_NL_gv

v_NL_gv_yr_gap <- ggplot(c_22_23, aes(x=factor(year), y=gv_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())
v_NL_gv_yr_gap

# compare leaf litter C bw years
summary(c_2022_compat$ll_carbon_9m2)
summary(c_2023_compat$ll_carbon_9m2)

ggplot(c_22_23, aes(x=factor(year), y=ll_carbon_9m2, colour = park_id)) + 
  geom_boxplot() + theme(legend.title = element_blank())

ggplot(c_22_23, aes(x=factor(year), y=ll_carbon_9m2, colour = gap)) + 
  geom_boxplot() + theme(legend.title = element_blank())

ggplot(c_22_23, aes(x=factor(year), y=ll_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())

# compare soil C bw years
summary(c_2022_compat$sl_carbon_9m2)[[4]]
summary(c_2023_compat$sl_carbon_9m2)[[4]]

sum(c_2022_compat$sl_carbon_9m2)
sum(c_2023_compat$sl_carbon_9m2)

summary(subset(c_2023_compat$sl_carbon_9m2, c_2023_compat$park_id == "GM"))[[4]]
summary(subset(c_2023_compat$sl_carbon_9m2, c_2023_compat$park_id == "TN"))[[4]]

ggplot(c_22_23, aes(x=factor(year), y=sl_carbon_9m2)) + 
  geom_boxplot() + theme(legend.title = element_blank())

summary(lm(c_22_23$sl_carbon_9m2 ~ as.factor(c_22_23$year)+c_22_23$park_id))

ggplot(c_22_23, aes(x=factor(year), y=sl_carbon_9m2, colour = park_id)) + 
  geom_boxplot() + theme(legend.title = element_blank())

ggplot(c_22_23, aes(x=factor(year), y=sl_carbon_9m2, colour = gap)) + 
  geom_boxplot() + theme(legend.title = element_blank())

ggplot(c_22_23, aes(x=factor(gap), y=sl_carbon_9m2, colour = gap)) + 
  geom_boxplot() + theme(legend.title = element_blank())

ggplot(c_22_23, aes(x=interaction(gap, park_id, sep=':'), y=sl_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())

summary(lm(c_22_23$sl_carbon_9m2 ~ c_22_23$gap))

ggplot(c_22_23, aes(x=factor(year), y=sl_carbon_9m2, colour = gap)) + 
  geom_violin() + theme(legend.title = element_blank())
ggplot(c_22_23, aes(x=factor(year), y=sl_carbon_9m2, colour = park_id)) + 
  geom_violin() + theme(legend.title = element_blank())

ggplot(subset(c_22_23,c_22_23$year == 2022), aes(sl_carbon_9m2)) +
         geom_histogram() +
  xlim(0, 250000)
ggplot(subset(c_22_23,c_22_23$year == 2023), aes(sl_carbon_9m2)) +
         geom_histogram()+
  xlim(0, 250000)
```

```{r}
# linear model
summary(lm(c_22_23$te_carbon_9m2 ~ as.factor(c_22_23$year)))
summary(lm(c_22_23$ss_carbon_9m2 ~ as.factor(c_22_23$year)))
summary(lm(c_22_23$dw_carbon_9m2 ~ as.factor(c_22_23$year)))
summary(lm(c_22_23$rt_carbon_9m2 ~ as.factor(c_22_23$year)))
summary(lm(c_22_23$gv_carbon_9m2 ~ as.factor(c_22_23$year)))
summary(lm(c_22_23$ll_carbon_9m2 ~ as.factor(c_22_23$year)))
summary(lm(c_22_23$sl_carbon_9m2 ~ as.factor(c_22_23$year)))
```

#### compare pools

```{r}

# for seperate years
l_c_22_23 <- pivot_longer(c_22_23, cols = 8:14, names_to = "c_pool", values_to = "c") %>%
  filter(c_pool != "sl_carbon_9m2") %>%
  filter(c_pool != "ll_carbon_9m2")

v_NL_all_pools <- ggplot(l_c_22_23, aes(x = gap, y = c, colour = c_pool)) + 
  geom_boxplot()
  
v_NL_all_pools

b_NL_all_pools <- ggplot(l_c_22_23, aes(x = gap, y = c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(c(0,30000000))
b_NL_all_pools

b_all_pools <- ggplot(l_c_22_23, aes(x = interaction(gap, park_id, sep=':'), y = c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(c(0,15000000))
b_all_pools



# for 2022
l_c_22 <- l_c_22_23 %>% 
  filter(year == 2022)

v_NL_22_pools <- ggplot(l_c_22, aes(x = gap, y = c, colour = c_pool)) + 
  geom_boxplot()
  
v_NL_22_pools

b_NL_22_pools <- ggplot(l_c_22, aes(x = gap, y = c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(c(0,15000000))
b_NL_22_pools

b_22_pools <- ggplot(l_c_22, aes(x = interaction(gap, park_id, sep=':'), y = c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(c(0,7500000))
b_22_pools

# for 2023
l_c_23 <- l_c_22_23 %>% 
  filter(year == 2023)

v_NL_23_pools <- ggplot(l_c_23, aes(x = gap, y = c, colour = c_pool)) + 
  geom_boxplot()
  
v_NL_23_pools

b_NL_23_pools <- ggplot(l_c_23, aes(x = gap, y = c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(c(0,15000000))
b_NL_23_pools

b_23_pools <- ggplot(l_c_23, aes(x = interaction(gap, park_id, sep=':'), y = c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(c(0,7500000))
b_23_pools
```

#### average of pools

```{r}
l_c_22_23_avg <- l_c_22_23 %>%
  group_by(park_id, year, gap, c_pool) %>%
  summarise(mean_c = mean(c))
l_c_22_avg <- l_c_22_23_avg %>%
  filter(year == 2022)
l_c_23_avg <- l_c_22_23_avg %>%
  filter(year == 2023)

b_all_pools_avg <- ggplot(l_c_22_23_avg, aes(x = gap, y = mean_c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(0,1000000)
b_all_pools_avg

b_all_pools_avg2 <- ggplot(l_c_22_23_avg, aes(x = interaction(gap, park_id, sep=':'), y = mean_c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(0,500000)
b_all_pools_avg2

b_22_pools_avg <- ggplot(l_c_22_avg, aes(x = gap, y = mean_c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(0,600000)
b_22_pools_avg

b_22_pools_avg2 <- ggplot(l_c_22_avg, aes(x = interaction(gap, park_id, sep=':'), y = mean_c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(0,400000)
b_22_pools_avg2

b_23_pools_avg <- ggplot(l_c_23_avg, aes(x = gap, y = mean_c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(0,600000)
b_23_pools_avg

b_23_pools_avg2 <- ggplot(l_c_23_avg, aes(x = interaction(gap, park_id, sep=':'), y = mean_c, colour = c_pool, fill = c_pool)) +
  geom_bar(stat = "identity") +
  ylim(0,400000)
b_23_pools_avg2

l_te_22_23_avg <- l_c_22_23 %>%
  group_by(park_id, year, gap, c_pool, site_id) %>%
  summarise(mean_c = mean(c)) %>%
  filter(c_pool == "te_carbon_9m2")

te_avg_NL_te <- ggplot(l_te_22_23_avg, aes(x= factor(year), y=mean_c)) + 
  geom_violin()
te_avg_NL_te


te_avg_te_yr_gap <- ggplot(l_te_22_23_avg, aes(x=factor(year), y=mean_c, colour = interaction(gap, park_id, sep=':'))) + 
  geom_boxplot() + theme(legend.title = element_blank())
te_avg_te_yr_gap
```

#### play around with shrubs and saplings

```{r}
# compare shrub and sapling C bw years
summary(c_2022_compat$ss_carbon_9m2)
summary(c_2023_compat$ss_carbon_9m2)

v_NL_ss <- ggplot(c_22_23, aes(x=factor(year), y=ss_carbon_9m2)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")
v_NL_ss

v_NL_ss_yr_gap <- ggplot(c_22_23, aes(x=factor(year), y=ss_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", position = "jitter",
               aes(colour = interaction(gap, park_id, sep=':'))) + theme(legend.title = element_blank())
v_NL_ss_yr_gap

ss_c_22_23 <- c_22_23 %>%
  filter(ss_carbon_9m2 <= 50000)
ss_c_2022_compat <- c_2022_compat %>%
  filter(ss_carbon_9m2 <= 50000)
ss_c_2023_compat <- c_2023_compat %>%
  filter(ss_carbon_9m2 <= 50000)

summary(ss_c_2022_compat$ss_carbon_9m2)
summary(ss_c_2023_compat$ss_carbon_9m2)

v_NL_ss2 <- ggplot(ss_c_22_23, aes(x=factor(year), y=ss_carbon_9m2)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
               colour = "red")
v_NL_ss2

v_NL_ss_yr_gap2 <- ggplot(ss_c_22_23, aes(x=factor(year), y=ss_carbon_9m2, colour = interaction(gap, park_id, sep=':'))) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", position = "jitter",
               aes(colour = interaction(gap, park_id, sep=':'))) + theme(legend.title = element_blank())
v_NL_ss_yr_gap2

# conclusion: it is the 3 really large values in 2023 driving the difference bewteen 2022 and 2023 *the large values are caused by big but short trees so they are considered saplings even if they are very wide

```
