---
title: "Complete run through"
author: "Emmerson Wilson"
date: "2024-01-18"
output:
 pdf_document:
   toc: true
   toc_depth: 5
classoption: landscape
---

```{r}
pacman::p_load(
  dplyr,
  tidyverse,
  readxl,
  cv,
  lme4,
  boot,
  MuMIn,
  sjPlot,
  AICcmodavg)
  
```

# data

# c at sites

```{r}
library(httr)

github_link1 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/c_m2_site.xlsx?raw=true"

temp_file1 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req1 <- GET(github_link1, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file1))
c_m2_sites <- read_xlsx(temp_file1)%>% 
  rename(unique_id = "id")
c_m2_sites

unlink(temp_file1)
```

# c at subplots

```{r}
github_link2 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/c_m2_subplot.xlsx?raw=true"

temp_file2 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req2 <- GET(github_link2, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file2))
c_m2_subplots <- read_xlsx(temp_file2)  
c_m2_subplots

unlink(temp_file2)
```

# environmental variables at sites

```{r}
github_link3 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/env_site_final.xlsx?raw=true"

temp_file3 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req3 <- GET(github_link3, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file3))
env_site_final <- read_xlsx(temp_file3)
env_site_final

unlink(temp_file3)

c_env_sites <- full_join(c_m2_sites, env_site_final) %>%
  dplyr::select(!c(FAC, CC, CEC_LCT, dominant))
c_env_sites$Moose_new <- as.character(c_env_sites$Moose_new)

  
#subset by park
c_env_sites_GM <- c_env_sites %>% 
  filter(park == "GM") 

c_env_sites_TN <- c_env_sites %>% 
  filter(park == "TN") 

#scale predictor variables (but don't center around 0)
c_env_sites_scale <- c_env_sites

c_env_sites_scale[c(11:16, 18)] <- scale(c_env_sites_scale[c(11:16, 18)], center = F)

c_env_sites_scale_GM <- c_env_sites_scale %>% 
  filter(park == "GM")

c_env_sites_scale_GM["Moose_new"][c_env_sites_scale_GM["Moose_new"] == 1] <- "aL"
c_env_sites_scale_GM["Moose_new"][c_env_sites_scale_GM["Moose_new"] == 2] <- "aL"
c_env_sites_scale_GM["Moose_new"][c_env_sites_scale_GM["Moose_new"] == 3] <- "bH"
c_env_sites_scale_GM["Moose_new"][c_env_sites_scale_GM["Moose_new"] == 4] <- "cX"

c_env_sites_scale_GM$Moose_new <- as.factor(c_env_sites_scale_GM$Moose_new)

c_env_sites_scale_TN <- c_env_sites_scale %>% 
  filter(park == "TN")

c_env_sites_scale_TN["Moose_new"][c_env_sites_scale_TN["Moose_new"] == 1] <- "aL"
c_env_sites_scale_TN["Moose_new"][c_env_sites_scale_TN["Moose_new"] == 2] <- "bM"
c_env_sites_scale_TN["Moose_new"][c_env_sites_scale_TN["Moose_new"] == 3] <- "cH"
c_env_sites_scale_TN["Moose_new"][c_env_sites_scale_TN["Moose_new"] == 4] <- "dV"

c_env_sites_scale_TN$Moose_new <- as.factor(c_env_sites_scale_TN$Moose_new)
```

# environmental variables at each subplot

```{r}
github_link4 <- "https://github.com/emmwilson/C_forecasting_NL/blob/main/final%20carbon%20data/env_subplots_final.xlsx?raw=true"

temp_file4 <- tempfile(tmpdir = getwd(), fileext = ".xlsx")
req4 <- GET(github_link4, 
           # authenticate using GITHUB_PAT
           authenticate(Sys.getenv("GITHUB_PAT"), ""),
           # write result to disk
           write_disk(path = temp_file4))
env_subplot_final <- read_xlsx(temp_file4)
env_subplot_final

unlink(temp_file4)

c_env_subplots <- full_join(c_m2_subplots, env_subplot_final) %>%
  dplyr::select(!c(FAC, CC, CEC_LCT, SPC))
c_env_subplots$Moose_new <- as.character(c_env_subplots$Moose_new)

#subset by park
c_env_subplots_GM <- c_env_subplots %>% 
  filter(park_id == "GM")


c_env_subplots_TN <- c_env_subplots %>% 
  filter(park_id == "TN")


# scale environmental variables (but don't center around 0)

c_env_sub_scale <- c_env_subplots

c_env_sub_scale[c(21:26, 28)] <- scale(c_env_sub_scale[c(21:26, 28)], center = F)

c_env_sub_scale_GM <- c_env_sub_scale %>% 
  filter(park_id == "GM")

c_env_sub_scale_GM["Moose_new"][c_env_sub_scale_GM["Moose_new"] == 1] <- "aL"
c_env_sub_scale_GM["Moose_new"][c_env_sub_scale_GM["Moose_new"] == 2] <- "aL"
c_env_sub_scale_GM["Moose_new"][c_env_sub_scale_GM["Moose_new"] == 3] <- "bH"
c_env_sub_scale_GM["Moose_new"][c_env_sub_scale_GM["Moose_new"] == 4] <- "cX"

c_env_sub_scale_GM$Moose_new <- as.factor(c_env_sub_scale_GM$Moose_new)

c_env_sub_scale_TN <- c_env_sub_scale %>% 
  filter(park_id == "TN") 

c_env_sub_scale_TN["Moose_new"][c_env_sub_scale_TN["Moose_new"] == 1] <- "aL"
c_env_sub_scale_TN["Moose_new"][c_env_sub_scale_TN["Moose_new"] == 2] <- "bM"
c_env_sub_scale_TN["Moose_new"][c_env_sub_scale_TN["Moose_new"] == 3] <- "cH"
c_env_sub_scale_TN["Moose_new"][c_env_sub_scale_TN["Moose_new"] == 4] <- "dV"

c_env_sub_scale_TN$Moose_new <- as.factor(c_env_sub_scale_TN$Moose_new)
```

# model functions

```{r}
source("https://github.com/emmwilson/C_forecasting_NL/blob/main/code_for_stats/lmer%20model%20functions.R?raw=true")

R2 <- function(model){
  with(summary(model), 1 - deviance/null.deviance)
}
```

# GM


## by site

### null

```{r}
#run the model
GM_lm_null <- lm_glm(c_env_sites_scale_GM, "c_m2_site", "1")

# get the summary of the model into a dataframe
GM_lm_null_summary <- as.data.frame(summary(GM_lm_null)$coefficients) %>% 
  mutate(model = "GM_lm_null") 
GM_lm_null_summary <- GM_lm_null_summary %>% 
  add_column("predictor" = rownames(GM_lm_null_summary))

# reorder columns so model name first
GM_lm_null_summary <- GM_lm_null_summary[,c(5,6,1:4)]
GM_lm_null_summary
```

### full

```{r}
# make list of all variables to be included in full model
full_var <- list("FHT", "EVIamp", "EVImed", "ELE", "SLO", "ASP", "LGS", "Moose_new")

# run the model
GM_lm_full <- lm_glm(c_env_sites_scale_GM, "c_m2_site", full_var)

# thoughts: FHT obviously important. seems no effect of moose levels - want to see if moose are correlated with forest height

# add summary of model to dataframe
GM_lm_full_summary <- as.data.frame(summary(GM_lm_full)$coefficients) %>% 
  mutate(model = "GM_lm_full") 
GM_lm_full_summary <- GM_lm_full_summary %>% 
  add_column("predictor" = rownames(GM_lm_full_summary))

GM_lm_full_summary <- GM_lm_full_summary[,c(5,6,1:4)]
GM_lm_full_summary
```

### univariate

```{r}
# run model with each predictor variable on own

GM_lm_uni <- lapply(full_var, lm_glm, df = c_env_sites_scale_GM, c = "c_m2_site")


names(GM_lm_uni) <- full_var # make sure names of objects in list consistent

GM_lm_uni_summary <- lapply(GM_lm_uni, summary)

GM_lm_uni_summary

#thoughts: FHT obviosuly important again. strange that full model had EVImed as sig but univariate has EVIamp as sig (will try diff combos of reduced to explore). 

```

## summary of uni, null and full

```{r}
# get summary of each univariate model, add them to a single dataframe with model name and variables in own columns


GM_uni_summary_all <- Reduce(full_join,lapply(mapply(cbind, lapply(lapply(GM_lm_uni_summary, coef), as.data.frame), "model"=names(GM_lm_uni_summary), SIMPLIFY=F), rownames_to_column, var = "predictor")) 
GM_uni_summary_all <- GM_uni_summary_all[,c(5,6,1:4)]
GM_uni_summary_all

# combine summary dataframes for null, full and univariate models
GM_lm_summary <- rbind(GM_lm_null_summary, GM_lm_full_summary, GM_uni_summary_all) 
GM_lm_summary <- GM_lm_summary %>% 
  mutate(significance = ifelse(GM_lm_summary$`Pr(>|t|)` < 0.001, "***", ifelse(GM_lm_summary$`Pr(>|t|)` < 0.01, "**", ifelse(GM_lm_summary$`Pr(>|t|)` < 0.05, "*", ifelse(GM_lm_summary$`Pr(>|t|)` < 0.1, ".", " "))))) # add symbols for easy visualization of sigificance
```


## compare

```{r}
# see excel "c_lm_model_results.xlsx" for consolidated values

# add univariate, null and full models into a list
GM_models_r <- list()

GM_models_r[["GM_lm_null"]] <- GM_lm_null
GM_models_r[["GM_lm_full"]] <- GM_lm_full
GM_models_r[[names(GM_lm_uni)[1]]] <- GM_lm_uni[[1]]
GM_models_r[[names(GM_lm_uni)[2]]] <- GM_lm_uni[[2]]
GM_models_r[[names(GM_lm_uni)[3]]] <- GM_lm_uni[[3]]
GM_models_r[[names(GM_lm_uni)[4]]] <- GM_lm_uni[[4]]
GM_models_r[[names(GM_lm_uni)[5]]] <- GM_lm_uni[[5]]
GM_models_r[[names(GM_lm_uni)[6]]] <- GM_lm_uni[[6]]
GM_models_r[[names(GM_lm_uni)[7]]] <- GM_lm_uni[[7]]
GM_models_r[[names(GM_lm_uni)[8]]] <- GM_lm_uni[[8]]

Modnames_GM_r <- paste(names(GM_models_r)) # make sure names are same as model name

# get table
aic_GM <- as.data.frame(aictab(cand.set = GM_models_r, modnames = Modnames_GM_r, sort = TRUE))

# try to add R2 to AIC table
R2_GM <- as.data.frame(sapply(GM_models_r, R2)) %>% setNames(c("R2"))
R2_GM <- R2_GM %>% 
   mutate("Modnames" = rownames(R2_GM))
R2_GM
aic_GM

aic_R2_GM <- full_join(aic_GM, R2_GM)

view(aic_R2_GM) # table of AIC values for null, full and univariate models

# thoughts: FHT staying strong. strange that EVImed has such high AIC but was sig in full model. AIC for EVIamp agrees with univariate model. 
```

### reduced

dropping one variable at a time, based on combination of significance in full model and AIC of univariate model. If values conflicting try removing two different variables and compare

```{r eval=FALSE, include=FALSE}
# see excel "c_lm_model_results.xlsx" for consolidated values

names(full_var) <- full_var

# make lists of variables to be tested in reduced models in order
GM_red_list1 <- within(full_var, rm("ELE"))
GM_red_list2 <- within(GM_red_list1, rm("ASP"))
GM_red_list3 <- within(GM_red_list2, rm("SLO"))
GM_red_list4 <- within(GM_red_list3, rm("Moose_new")) # taking out moose made EVImed more significant
GM_red_list5 <- within(GM_red_list4, rm("EVImed"))
GM_red_list6 <- within(GM_red_list4, rm("EVIamp")) # tried removing, EVImed, EVIamp and LGS and compare (best was removing LGS). also just removing EVIamp made EVImed less significant
GM_red_list7 <- within(GM_red_list4, rm("LGS"))
GM_red_list8 <- within(GM_red_list7, rm("EVImed"))
GM_red_list9 <- within(GM_red_list7, rm("EVIamp")) 

# add lists of variables to a metalist
GM_red_list <- list(GM_red_list1, GM_red_list2, GM_red_list3, GM_red_list4, GM_red_list5, GM_red_list6, GM_red_list7, GM_red_list8, GM_red_list9)


# run glm on each combination of variables
GM_lm_red <- lapply(GM_red_list, lm_glm, df = c_env_sites_scale_GM, c = "c_m2_site")

names(GM_lm_red) <- lapply(GM_red_list, paste0, collapse = " + ") # name each object 

GM_lm_red_summary <- lapply(GM_lm_red, summary) # get summary of each reduced model
GM_lm_red_summary

Modnames_GM_red_r <- names(GM_lm_red)

# aic for reduced models
aic_GM_red <- as.data.frame(aictab(cand.set = GM_lm_red, modnames = Modnames_GM_red_r, sort = TRUE))

# r2 for reduced models
R2_GM_red<- as.data.frame(sapply(GM_lm_red, R2)) %>% setNames(c("R2"))
R2_GM_red <- R2_GM_red %>% mutate("Modnames" = rownames(R2_GM_red))

aic_R2_GM_red <- full_join(aic_GM_red, R2_GM_red)

view(aic_R2_GM_red)

# aic for all models
aic_GM_all <- as.data.frame(aictab(cand.set = c(GM_models_r, GM_lm_red), modnames = names(c(GM_models_r, GM_lm_red)), sort = TRUE))

# r2 for all models
R2_GM_all <- rbind(R2_GM, R2_GM_red)

aic_R2_GM_all <- full_join(aic_GM_all, R2_GM_all)

# final table of AIC and r2 for GM
view(aic_R2_GM_all)

```

## by subplot

### null

```{r}
# fixed effects - very much pseaudoreplication but ran the models out of curiosity
GM_lm_null_subfe <- lm_glm(c_env_sub_scale_GM, "c_m2_subplot", "1")

summary(GM_lm_null_subfe)

# mixed effects
GM_lm_null_sub <- lm_lmer(c_env_sub_scale_GM, "c_m2_subplot", "1")

GM_lm_null_sub_summary <- summary(GM_lm_null_sub)
r.squaredGLMM(GM_lm_null_sub)
```

### full

```{r}
# fixed effects

GM_lm_full_subfe <- lm_glm(c_env_sub_scale_GM, "c_m2_subplot", full_var)
summary(GM_lm_full_subfe)

# mixed effects
GM_lm_full_sub <- lm_lmer(c_env_sub_scale_GM, "c_m2_subplot", full_var)

summary(GM_lm_full_sub)
r.squaredGLMM(GM_lm_full_sub)
```

### univariate

```{r}
# fixed effects

GM_lm_uni_subfe <- lapply(full_var, lm_glm, df = c_env_sub_scale_GM, c = "c_m2_subplot")

names(GM_lm_uni_subfe) <- full_var

GM_lm_uni_subfe_summary <- lapply(GM_lm_uni_subfe, summary)
GM_lm_uni_subfe_summary

# mixed effects

GM_lm_uni_sub <- lapply(full_var, lm_lmer, df = c_env_sub_scale_GM, c = "c_m2_subplot")

names(GM_lm_uni_sub) <- full_var

GM_lm_uni_sub_summary <- lapply(GM_lm_uni_sub, summary)

GM_lm_uni_sub_r2 <- lapply(GM_lm_uni_sub, r.squaredGLMM)
GM_lm_uni_sub_r2
```

## compare

```{r}
GM_models_subfe_r <- list()

GM_models_subfe_r[["GM_lm_null_subfe"]] <- GM_lm_null_subfe
GM_models_subfe_r[["GM_lm_full_subfe"]] <- GM_lm_full_subfe
GM_models_subfe_r[[names(GM_lm_uni_subfe)[1]]] <- GM_lm_uni_subfe[[1]]
GM_models_subfe_r[[names(GM_lm_uni_subfe)[2]]] <- GM_lm_uni_subfe[[2]]
GM_models_subfe_r[[names(GM_lm_uni_subfe)[3]]] <- GM_lm_uni_subfe[[3]]
GM_models_subfe_r[[names(GM_lm_uni_subfe)[4]]] <- GM_lm_uni_subfe[[4]]
GM_models_subfe_r[[names(GM_lm_uni_subfe)[5]]] <- GM_lm_uni_subfe[[5]]
GM_models_subfe_r[[names(GM_lm_uni_subfe)[6]]] <- GM_lm_uni_subfe[[6]]
GM_models_subfe_r[[names(GM_lm_uni_subfe)[7]]] <- GM_lm_uni_subfe[[7]]
GM_models_subfe_r[[names(GM_lm_uni_subfe)[8]]] <- GM_lm_uni_subfe[[8]]

Modnames_GM_subfe_r <- paste(names(GM_models_subfe_r))

# get table
aic_GM_sub_fe <- aictab(cand.set = GM_models_subfe_r, modnames = Modnames_GM_subfe_r, sort = TRUE)
  # mutate(R2m = sapply(lapply(GM_models_subfe_r, r.squaredGLMM), "[[", 1)) %>% 
  # mutate(R2c = sapply(lapply(GM_models_subfe_r, r.squaredGLMM), "[[", 2))


GM_models_sub_r <- list()

GM_models_sub_r[["GM_lm_null_sub"]] <- GM_lm_null_sub
GM_models_sub_r[["GM_lm_full_sub"]] <- GM_lm_full_sub
GM_models_sub_r[[names(GM_lm_uni_sub)[1]]] <- GM_lm_uni_sub[[1]]
GM_models_sub_r[[names(GM_lm_uni_sub)[2]]] <- GM_lm_uni_sub[[2]]
GM_models_sub_r[[names(GM_lm_uni_sub)[3]]] <- GM_lm_uni_sub[[3]]
GM_models_sub_r[[names(GM_lm_uni_sub)[4]]] <- GM_lm_uni_sub[[4]]
GM_models_sub_r[[names(GM_lm_uni_sub)[5]]] <- GM_lm_uni_sub[[5]]
GM_models_sub_r[[names(GM_lm_uni_sub)[6]]] <- GM_lm_uni_sub[[6]]
GM_models_sub_r[[names(GM_lm_uni_sub)[7]]] <- GM_lm_uni_sub[[7]]
GM_models_sub_r[[names(GM_lm_uni_sub)[8]]] <- GM_lm_uni_sub[[8]]

Modnames_GM_sub_r <- paste(names(GM_models_sub_r))

# get table
 aic_GM_sub <- aictab(cand.set = GM_models_sub_r, modnames = Modnames_GM_sub_r, sort = TRUE) 
 
R2_GM_sub <- as.data.frame(sapply(GM_models_sub_r, r.squaredGLMM)) %>% t() %>%  as.data.frame() %>% setNames(c("R2m", "R2c"))
R2_GM_sub <- R2_GM_sub %>% 
   mutate("Modnames" = rownames(R2_GM_sub))

aic_R2_GM_sub <- full_join(aic_GM_sub, R2_GM_sub)


```

### reduced

```{r eval=FALSE, include=FALSE}
names(full_var) <- full_var

GM_sub_red_list1 <- within(full_var, rm("ELE"))
GM_sub_red_list2 <- within(GM_sub_red_list1, rm("SLO"))
GM_sub_red_list3 <- within(GM_sub_red_list2, rm("Moose_new"))
GM_sub_red_list4 <- within(GM_sub_red_list3, rm("EVImed")) #would be weird if important in non-mixed model but not here, it is worse than keeping it so try removing a different variable
GM_sub_red_list5 <- within(GM_sub_red_list3, rm("ASP")) # even worse
GM_sub_red_list6 <- within(GM_sub_red_list3, rm("EVIamp")) 
GM_sub_red_list7 <- within(GM_sub_red_list3, rm("LGS")) # taking away EVIamp or LGS basically the same so try both
GM_sub_red_list8 <- within(GM_sub_red_list6, rm("LGS")) 
GM_sub_red_list9 <- within(GM_sub_red_list8, rm("ASP")) # bad
GM_sub_red_list10 <- within(GM_sub_red_list8, rm("EVImed"))

GM_sub_red_list <- list(GM_sub_red_list1, GM_sub_red_list2, GM_sub_red_list3, GM_sub_red_list4, GM_sub_red_list5, GM_sub_red_list6, GM_sub_red_list7, GM_sub_red_list8, GM_sub_red_list9, GM_sub_red_list10)

GM_sub_lm_red <- lapply(GM_sub_red_list, lm_lmer, df = c_env_sub_scale_GM, c = "c_m2_subplot")

names(GM_sub_lm_red) <- lapply(GM_sub_red_list, paste0, collapse = " + ") # make names of functions the formula not list of "var = var"

GM_sub_lm_red_summary <- lapply(GM_sub_lm_red, summary)
GM_sub_lm_red_summary

Modnames_GM_sub_red_r <- names(GM_sub_lm_red)
#this calculates corrected AIC so slightly different values than normal AIC

# table for just reduced models
aic_GM_sub_red <- aictab(cand.set = GM_sub_lm_red, modnames = Modnames_GM_sub_red_r, sort = TRUE) 

R2_GM_sub_red <- as.data.frame(sapply(GM_sub_lm_red, r.squaredGLMM)) %>% t() %>%  as.data.frame() %>% setNames(c("R2m", "R2c"))
R2_GM_sub_red <- R2_GM_sub_red %>% 
   mutate("Modnames" = rownames(R2_GM_sub_red))

aic_R2_GM_sub_red <- full_join(aic_GM_sub_red, R2_GM_sub_red)

# table for all models
aic_GM_sub_all <- aictab(cand.set = c(GM_models_sub_r, GM_sub_lm_red), modnames = c(Modnames_GM_sub_r, Modnames_GM_sub_red_r), sort = TRUE) 

R2_GM_sub_all <- rbind(R2_GM_sub, R2_GM_sub_red)

aic_R2_GM_sub_all <- full_join(aic_GM_sub_all, R2_GM_sub_all)

view(aic_R2_GM_sub_all)
```

# TN

# temporarily setTN 05

```{r}
c_env_sites_scale_TN$Moose_new <-replace_na(c_env_sites_scale_TN$Moose_new, "cH")

c_env_sub_scale_TN$Moose_new <-replace_na(c_env_sub_scale_TN$Moose_new, "cH")
```


## by site

### null

```{r}
TN_lm_null <- lm_glm(c_env_sites_scale_TN, "c_m2_site", "1")

summary(TN_lm_null)

# make into data frame that can be combined with other mdoels'
TN_lm_null_summary <- as.data.frame(summary(TN_lm_null)$coefficients) %>% 
  mutate(model = "TN_lm_null") 
TN_lm_null_summary <- TN_lm_null_summary %>% 
  add_column("predictor" = rownames(TN_lm_null_summary))

TN_lm_null_summary <- TN_lm_null_summary[,c(5,6,1:4)]
TN_lm_null_summary
```

### full

```{r}

TN_lm_full <- lm_glm(c_env_sites_scale_TN, "c_m2_site", full_var)

summary(TN_lm_full)

TN_lm_full_summary <- as.data.frame(summary(TN_lm_full)$coefficients) %>% 
  mutate(model = "TN_lm_full") 
TN_lm_full_summary <- TN_lm_full_summary %>% 
  add_column("predictor" = rownames(TN_lm_full_summary))

TN_lm_full_summary <- TN_lm_full_summary[,c(5,6,1:4)]
TN_lm_full_summary

# thoughts: forest height important again. This time EVIamp also sig in full model.
```

### univariate

```{r}

TN_lm_uni <- lapply(full_var, lm_glm, df = c_env_sites_scale_TN, c = "c_m2_site")

names(TN_lm_uni) <- full_var

TN_lm_uni_summary <- lapply(TN_lm_uni, summary)
TN_lm_uni_summary
# thoughts: FHT same as always. but now EVIamp not sig, but slope is. 

```

## summary of uni, null and full

```{r}
# get summary of each univariate model, add them to a single dataframe with model name and variables in own columns


TN_uni_summary_all <- Reduce(full_join,lapply(mapply(cbind, lapply(lapply(TN_lm_uni_summary, coef), as.data.frame), "model"=names(TN_lm_uni_summary), SIMPLIFY=F), rownames_to_column, var = "predictor")) 
TN_uni_summary_all <- TN_uni_summary_all[,c(5,6,1:4)]
TN_uni_summary_all

# combine summary dataframes for null, full and univariate models
TN_lm_summary <- rbind(TN_lm_null_summary, TN_lm_full_summary, TN_uni_summary_all) 
TN_lm_summary <- TN_lm_summary %>% 
  mutate(significance = ifelse(TN_lm_summary$`Pr(>|t|)` < 0.001, "***", ifelse(TN_lm_summary$`Pr(>|t|)` < 0.01, "**", ifelse(TN_lm_summary$`Pr(>|t|)` < 0.05, "*", ifelse(TN_lm_summary$`Pr(>|t|)` < 0.1, ".", " "))))) # add symbols for easy visualization of sigificance
```

## compare

```{r}
# see excel "c_lm_model_results.xlsx" for consolidated values

TN_models_r <- list()

TN_models_r[["TN_lm_null"]] <- TN_lm_null
TN_models_r[["TN_lm_full"]] <- TN_lm_full
TN_models_r[[names(TN_lm_uni)[1]]] <- TN_lm_uni[[1]]
TN_models_r[[names(TN_lm_uni)[2]]] <- TN_lm_uni[[2]]
TN_models_r[[names(TN_lm_uni)[3]]] <- TN_lm_uni[[3]]
TN_models_r[[names(TN_lm_uni)[4]]] <- TN_lm_uni[[4]]
TN_models_r[[names(TN_lm_uni)[5]]] <- TN_lm_uni[[5]]
TN_models_r[[names(TN_lm_uni)[6]]] <- TN_lm_uni[[6]]
TN_models_r[[names(TN_lm_uni)[7]]] <- TN_lm_uni[[7]]
TN_models_r[[names(TN_lm_uni)[8]]] <- TN_lm_uni[[8]]

Modnames_TN_r <- paste(names(TN_models_r))

# get table
aic_TN <- aictab(cand.set = TN_models_r, modnames = Modnames_TN_r, sort = TRUE)  
  # mutate(R2 = lapply(TN_models_r, R2))
view(aic_TN)

R2_TN <- as.data.frame(sapply(TN_models_r, R2)) %>% setNames(c("R2"))
R2_TN <- R2_TN %>% 
   mutate("Modnames" = rownames(R2_TN))
R2_TN
aic_TN

aic_R2_TN <- full_join(aic_TN, R2_TN)

view(aic_R2_TN) # table of AIC values for null, full and univariate models

# thoughts: FHT important again. also, even though moose univariate model is the worst AIC, it is actually important for reduced models (see below)
```

### reduced

```{r eval=FALSE, include=FALSE}

# see excel "c_lm_model_results.xlsx" for consolidated values

names(full_var) <- full_var

TN_red_list1 <- within(full_var, rm("ASP")) # taking away ASP made moose more sig
TN_red_list2 <- within(TN_red_list1, rm("ELE"))
TN_red_list3 <- within(TN_red_list2, rm("EVImed")) # taking away EVImed made the AIC even lower that just FHT, and made EVIamp more sig
TN_red_list4 <- within(TN_red_list2, rm("Moose_new")) # made AIC worst of reduced so keep in for now
TN_red_list6 <- within(TN_red_list3, rm("SLO")) #slope is only significant in univariate models
TN_red_list7 <- within(TN_red_list6, rm("EVIamp")) #not sure which to take out next so try each
TN_red_list8 <- within(TN_red_list6, rm("LGS"))
TN_red_list9 <- within(TN_red_list6, rm("Moose_new")) # taking out moose doesn't seem to help ever
TN_red_list10 <- within(TN_red_list8, rm("Moose_new"))
TN_red_list11 <- within(TN_red_list8, rm("EVIamp"))

TN_red_list <- list(TN_red_list1, TN_red_list2, TN_red_list3, TN_red_list4, TN_red_list6, TN_red_list7, TN_red_list8, TN_red_list9, TN_red_list10, TN_red_list11)

TN_lm_red <- lapply(TN_red_list, lm_glm, df = c_env_sites_scale_TN, c = "c_m2_site")
names(TN_lm_red) <- lapply(TN_red_list, paste0, collapse = " + ") 

TN_lm_red_summary <- lapply(TN_lm_red, summary)
TN_lm_red_summary

Modnames_TN_red_r <- names(TN_lm_red)

aic_TN_red <- aictab(cand.set = TN_lm_red, modnames = Modnames_TN_red_r, sort = TRUE) 

aic_TN_all <- aictab(cand.set = c(TN_models_r, TN_lm_red), modnames = c(Modnames_TN_r, Modnames_TN_red_r), sort = TRUE) 
 # mutate(R2 = lapply(c(TN_models_r, TN_lm_red), R2))

R2_TN_red <- as.data.frame(sapply(TN_lm_red, R2)) %>% setNames(c("R2"))
R2_TN_red <- R2_TN_red %>% 
   mutate("Modnames" = rownames(R2_TN_red))
R2_TN_all <- rbind(R2_TN, R2_TN_red)

aic_R2_TN_all <- full_join(aic_TN_all, R2_TN_all)

view(aic_R2_TN_all) # table of AIC values for null, full and univariate models


# EVIamp is only sig as long as moose AND LGS are in the model, if either are taken away EVIamp becomes insig

```

## by subplot

### null

```{r}
# fixed effects

TN_lm_null_subfe <- lm_glm(c_env_sub_scale_TN, "c_m2_subplot", "1")

# mixed effects
TN_lm_null_sub <- lm_lmer(c_env_sub_scale_TN, "c_m2_subplot", "1")

```

### full

```{r}
# fixed effects

TN_lm_full_subfe <- lm_glm(c_env_sub_scale_TN, "c_m2_subplot", full_var)
summary(TN_lm_full_subfe)

# mixed effects
TN_lm_full_sub <- lm_lmer(c_env_sub_scale_TN, "c_m2_subplot", full_var)

summary(TN_lm_full_sub)
r.squaredGLMM(TN_lm_full_sub)
```

### univariate

```{r}
# fixed effects

TN_lm_uni_subfe <- lapply(full_var, lm_glm, df = c_env_sub_scale_TN, c = "c_m2_subplot")

names(TN_lm_uni_subfe) <- full_var


TN_lm_uni_subfe_summary <- lapply(TN_lm_uni_subfe, summary)
TN_lm_uni_subfe_summary

# mixed effects

TN_lm_uni_sub <- lapply(full_var, lm_lmer, df = c_env_sub_scale_TN, c = "c_m2_subplot")

names(TN_lm_uni_sub) <- full_var

TN_lm_uni_sub_summary <- lapply(TN_lm_uni_sub, summary)

TN_lm_uni_sub_r2 <- lapply(TN_lm_uni_sub, r.squaredGLMM)
TN_lm_uni_sub_r2
```

## compare

```{r}
TN_models_subfe_r <- list()

TN_models_subfe_r[["TN_lm_null_subfe"]] <- TN_lm_null_subfe
TN_models_subfe_r[["TN_lm_full_subfe"]] <- TN_lm_full_subfe
TN_models_subfe_r[[names(TN_lm_uni_subfe)[1]]] <- TN_lm_uni_subfe[[1]]
TN_models_subfe_r[[names(TN_lm_uni_subfe)[2]]] <- TN_lm_uni_subfe[[2]]
TN_models_subfe_r[[names(TN_lm_uni_subfe)[3]]] <- TN_lm_uni_subfe[[3]]
TN_models_subfe_r[[names(TN_lm_uni_subfe)[4]]] <- TN_lm_uni_subfe[[4]]
TN_models_subfe_r[[names(TN_lm_uni_subfe)[5]]] <- TN_lm_uni_subfe[[5]]
TN_models_subfe_r[[names(TN_lm_uni_subfe)[6]]] <- TN_lm_uni_subfe[[6]]
TN_models_subfe_r[[names(TN_lm_uni_subfe)[7]]] <- TN_lm_uni_subfe[[7]]
TN_models_subfe_r[[names(TN_lm_uni_subfe)[8]]] <- TN_lm_uni_subfe[[8]]


Modnames_TN_subfe_r <- paste(names(TN_models_subfe_r))

# get table
aic_TN_sub_fe <- aictab(cand.set = TN_models_subfe_r, modnames = Modnames_TN_subfe_r, sort = TRUE)

# for mixed effects

TN_models_sub_r <- list()

TN_models_sub_r[["TN_lm_null_sub"]] <- TN_lm_null_sub
TN_models_sub_r[["TN_lm_full_sub"]] <- TN_lm_full_sub
TN_models_sub_r[[names(TN_lm_uni_sub)[1]]] <- TN_lm_uni_sub[[1]]
TN_models_sub_r[[names(TN_lm_uni_sub)[2]]] <- TN_lm_uni_sub[[2]]
TN_models_sub_r[[names(TN_lm_uni_sub)[3]]] <- TN_lm_uni_sub[[3]]
TN_models_sub_r[[names(TN_lm_uni_sub)[4]]] <- TN_lm_uni_sub[[4]]
TN_models_sub_r[[names(TN_lm_uni_sub)[5]]] <- TN_lm_uni_sub[[5]]
TN_models_sub_r[[names(TN_lm_uni_sub)[6]]] <- TN_lm_uni_sub[[6]]
TN_models_sub_r[[names(TN_lm_uni_sub)[7]]] <- TN_lm_uni_sub[[7]]
TN_models_sub_r[[names(TN_lm_uni_sub)[8]]] <- TN_lm_uni_sub[[8]]


Modnames_TN_sub_r <- paste(names(TN_models_sub_r))

# get table
aic_TN_sub <- aictab(cand.set = TN_models_sub_r, modnames = Modnames_TN_sub_r, sort = TRUE) 
view(aic_TN_sub)

R2_TN_sub<- as.data.frame(sapply(TN_models_sub_r, r.squaredGLMM)) %>% t() %>%  as.data.frame() %>% setNames(c("R2m", "R2c"))
R2_TN_sub <- R2_TN_sub %>% mutate("Modnames" = rownames(R2_TN_sub))
```

### reduced

```{r eval=FALSE, include=FALSE}
names(full_var) <- full_var

TN_sub_red_list1 <- within(full_var, rm("ELE"))

TN_sub_red_list <- list(full_var, TN_sub_red_list1)

TN_sub_lm_red <- lapply(TN_sub_red_list, lm_lmer, df = c_env_sub_scale_TN, c = "c_m2_subplot")
names(TN_sub_lm_red) <- lapply(TN_sub_red_list, paste0, collapse = " + ") 

TN_sub_lm_red_summary <- lapply(TN_sub_lm_red, summary)
TN_sub_lm_red_summary

Modnames_TN_sub_red_r <- names(TN_sub_lm_red)

aic_TN_sub_red <- aictab(cand.set = TN_sub_lm_red, modnames = Modnames_TN_sub_red_r, sort = TRUE) 

R2_TN_sub_red<- as.data.frame(sapply(TN_sub_lm_red, r.squaredGLMM)) %>% t() %>%  as.data.frame() %>% setNames(c("R2m", "R2c"))
R2_TN_sub_red <- R2_TN_sub_red %>% mutate("Modnames" = rownames(R2_TN_sub_red))

# table for all models
aic_TN_sub_all <- aictab(cand.set = c(TN_models_sub_r, TN_sub_lm_red), modnames = c(Modnames_TN_sub_r, Modnames_TN_sub_red_r), sort = TRUE) 



R2_TN_sub_all <- rbind(R2_TN_sub, R2_TN_sub_red)

aic_R2_TN_sub_all <- full_join(aic_TN_sub_all, R2_TN_sub_all)

view(aic_R2_TN_sub_all)

view(aic_TN_sub_all)
```
