---
title: "disturb vs not"
author: "Emmerson Wilson"
date: "2024-02-05"
output: html_document
---

```{r}
pacman::p_load(
  dplyr,
  tidyverse,
  readxl,
  cv,
  lme4,
  janitor)
  
```

# data

## 2022
```{r}
#combine individual excel files fror carbon in each pool
c_2022_dw <- read_xlsx("../final carbon data/Final_Carbon_Data_R/Rachael 2022 measurements/Deadwood_Field_Data NEW.xlsm", sheet = "DW carbon") %>%
  dplyr::select(c(Site_Subplot_ID, dw_carbon_9m2))
c_2022_te <- read_xlsx("../final carbon data/Final_Carbon_Data_R/Rachael 2022 measurements/Tree_Biomass_NEW.xlsm", sheet = "Tree carbon") %>%
  dplyr::select(c(Site_Subplot_ID, te_carbon_9m2))
c_2022_gc <- read_xlsx("../final carbon data/Final_Carbon_Data_R/ground_cover_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, gc_carbon_9m2))
c_2022_hb <- read_xlsx("../final carbon data/Final_Carbon_Data_R/herbaceous_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, hb_carbon_9m2))
c_2022_ll <- read_xlsx("../final carbon data/Final_Carbon_Data_R/litter_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Park_ID, Site_ID, Ex_Ctrl, Subplot_ID, Site_Subplot_ID, ll_carbon_9m2))
c_2022_sp <- read_xlsx("../final carbon data/Final_Carbon_Data_R/sapling_carbon.xlsx", sheet = "Sheet 1") %>% dplyr::select(c(Site_Subplot_ID, sp_carbon_9m2))
#c_2022_sr <- read_xlsx("Final_Carbon_Data_R/shrub_root_carbon.xlsx", sheet = "Sheet 1") because this data came before R fixed the under 30 units I need to calculate on my own
c_2022_sl <- read_xlsx("../final carbon data/Final_Carbon_Data_R/soil_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, sl_carbon_9m2))

c_2022_tr <- read_xlsx("../final carbon data/Final_Carbon_Data_R/Rachael 2022 measurements/Tree_Biomass_NEW.xlsm", sheet = "Tree root carbon") %>%
  dplyr::select(c(Site_Subplot_ID, tr_carbon_9m2))
c_2022_u3 <- read_xlsx("../final carbon data/Final_Carbon_Data_R/under_30_carbon.xlsx", sheet = "Sheet 1") %>%
  mutate(u3_carbon_9m2 = u3_carbon_9m2/1000000) %>% # convert units
  dplyr::select(c(Site_Subplot_ID, u3_carbon_9m2))
c_2022_ws <- read_xlsx("../final carbon data/Final_Carbon_Data_R/woody_shrubs_carbon.xlsx", sheet = "Sheet 1") %>%
  dplyr::select(c(Site_Subplot_ID, ws_carbon_9m2))
site_data_2022 <- read_xlsx("../final carbon data/Final_Carbon_Data_R/subplot_disturbacne.xlsx")

c_2022_sr_list <- list(c_2022_u3, c_2022_ws, c_2022_sp)
c_2022_sr <- c_2022_sr_list %>% reduce(full_join, by='Site_Subplot_ID') %>%
  replace(is.na(.), 0)
c_2022_sr$sr_carbon_9m2 <- rowSums(c_2022_sr[, c(2:4)])
c_2022_sr <- c_2022_sr %>% dplyr::select(c(1,5)) %>%
  mutate(sr_carbon_9m2 = sr_carbon_9m2*0.25)
  

c_2022_list <- list(c_2022_dw, c_2022_te, c_2022_gc, c_2022_hb, c_2022_ll, c_2022_sp, c_2022_sr, c_2022_sl, c_2022_tr, c_2022_u3, c_2022_ws)

c_2022 <- c_2022_list %>% reduce(full_join, by='Site_Subplot_ID') %>%
  dplyr::select(c(1,6:9,2:5,10:16)) %>%
  replace(is.na(.), 0)
c_2022$total_c_per_subplot <- rowSums(c_2022[, c(6:16)])

c_2022_mess <- c_2022 %>%
  left_join(site_data_2022) %>% # add subplot info
  clean_names() %>%
  mutate(gap = disturbance) %>% 
  mutate(across('gap', str_replace, 'Insect', 'Gap')) %>% # add if gap or not gap
  mutate(across('gap', str_replace, 'Fire', 'Gap')) %>%
  mutate(ss_carbon_9m2 = rowSums(c_2022[, c("sp_carbon_9m2", "ws_carbon_9m2")])) %>% # recategorize pools to match 2023
  mutate(rt_carbon_9m2 = rowSums(c_2022[, c("tr_carbon_9m2","sr_carbon_9m2")])) %>%
  mutate(gv_carbon_9m2 = rowSums(c_2022[, c("gc_carbon_9m2", "hb_carbon_9m2", "u3_carbon_9m2")])) %>%
  mutate(year = 2022) %>% # add year
  mutate(site_number = as.numeric(site_id))
c_2022_mess$site_number <- sprintf("%02.f", c_2022_mess$site_number)
c_2022_mess <- c_2022_mess %>%
  mutate(site_id = paste0(site_number, "_", "2022")) %>% # distinguish overlapping site numbers by year
  mutate(subplot_id = substr(subplot_id,2,2)) # remove letter from subplot

```

## 2023
```{r}
c_2023 <- read_xlsx("../final carbon data/carbon_data_2023.xlsm", sheet = "Overall C") %>%
  replace(is.na(.), 0) 

site_data <- read_xlsx("../final carbon data/carbon_data_2023.xlsm", sheet = "Subplot info")
site_data$Site_ID <- sprintf("%02.f", site_data$Site_ID)

c_2023_mess <- c_2023 %>%
  left_join(site_data)%>%
  clean_names() %>%
  mutate(gap = disturbance) %>%
  mutate(across('gap', str_replace, 'Insect', 'Gap')) %>% # add if gap or not gap
  mutate(across('gap', str_replace, 'Fire', 'Gap')) %>%
  mutate(across('gap', str_replace, 'Wind', 'Gap')) %>%
  mutate(across('gap', str_replace, 'Logging', 'Gap')) %>%
  mutate(year = 2023) %>% # add year
  mutate(site_id = paste0(site_id, "_", "2023")) # distinguish overlapping site numbers by year
  
```


```{r}
c_2022_compare <- c_2022_mess %>%
   dplyr::select(c(2:5,18,19,23,6,7,10,13,20:22,17)) # run "C_explore_22_23.qmd" first
c_2023_compare <- c_2023_mess %>%
  dplyr::select(c(22,23,25,2,27,38,39,5,7,10,11,13,16,18,21)) %>%
  replace(is.na(.), 0)
c_22_23 <- rbind(c_2022_compare, c_2023_compare) %>%
  mutate(unique_id = paste0(park_id, "_", site_id, "_", subplot_id))
```

# insect

## GM
the difference between insect gap exclosures and novel mature stands, to try to get at effect of only insects
```{r}
c_22_23_insectGM <- c_22_23 %>% 
  filter(park_id == "GM") %>% 
  filter(disturbance == "Insect" | disturbance ==  "Mature") %>% 
  filter(gap != "Gap" | ex_ctrl != "NA") %>% 
  filter(gap != "Mature" | ex_ctrl != "EX") %>% 
  filter(ex_ctrl != "CTRL") %>% 
  mutate(new_tot = total_c_per_subplot - dw_carbon_9m2) %>% 
  select(-c(dw_carbon_9m2, total_c_per_subplot)) 

# ggplot(c_22_23_insectGM, aes(x=factor(disturbance), y=total_c_per_subplot/9)) +
#   geom_violin()+
#   stat_summary(fun.data = "mean_cl_boot", geom = "pointrange")

mean_c_insectGM <- c_22_23_insectGM %>% 
  group_by(disturbance) %>% 
  summarize(mean = mean(new_tot/9))

less_c_insectGM <- mean_c_insectGM$mean[2]-mean_c_insectGM$mean[1] # per square meter there is on average 6738 less grams of carbon in a cell that is insect disturbed by only insects (no herbivory) in Gros Morne

less_c_insectGM*(7.976e+7)/1000 # total kg carbon lost by only insects in GM
```

## TN
the difference between insect gap exclosures and novel mature stands, to try to get at effect of only insects
```{r}
c_22_23_insectTN <-  c_22_23  %>% 
  filter(park_id == "TN") %>% 
  filter(disturbance == "Insect" | disturbance ==  "Mature") %>% 
  filter(gap != "Gap" | ex_ctrl != "NA") %>% 
  filter(gap != "Mature" | ex_ctrl != "EX") %>% 
  filter(ex_ctrl != "CTRL")  %>% 
  mutate(new_tot = total_c_per_subplot - dw_carbon_9m2) %>% 
  select(-c(dw_carbon_9m2, total_c_per_subplot)) 

#ggplot(c_22_23_insectTN, aes(x=factor(disturbance), y=total_c_per_subplot/9)) + 
  # geom_violin()+
  # stat_summary(fun.data = "mean_cl_boot", geom = "pointrange")

summary(lm(new_tot ~ disturbance, data = c_22_23_insectTN))

mean_c_insectTN <- c_22_23_insectTN %>% 
  group_by(disturbance) %>% 
  summarize(mean = mean(new_tot/9))

less_c_insectTN <- mean_c_insectTN$mean[2]-mean_c_insectTN$mean[1] # per square meter there is on average 18443 less grams of carbon in a cell that is insect disturbed in Terra Nova

less_c_insectTN*(1.3e+7)/1000 # total carbon lost by insects in TN
```

insect gaps in Terra Nova seem to have less carbon

# moose
```{r}
# none of the following code is paired

# c_22_23_moose <- c_22_23 %>% 
#   filter(ex_ctrl %in% c("CTRL", "EX")) %>% 
#   filter(site_id != "13_2022")
# 
# ggplot(c_22_23_moose, aes(x=factor(ex_ctrl), y=total_c_per_subplot/9)) + 
#   geom_violin()+
#   stat_summary(fun.data = "mean_cl_boot", geom = "pointrange")
# 
# mean_c_moose <- c_22_23_moose %>% 
#   group_by(ex_ctrl) %>% 
#   summarize(mean = mean(total_c_per_subplot/9))
# 
# summary(lm(c_22_23_moose$total_c_per_subplot/9 ~ c_22_23_moose$ex_ctrl)) # not statistically significant
# # maybe different pools?
# 
# 
# pools <- list("dw_carbon_9m2", "te_carbon_9m2", "ll_carbon_9m2", "sl_carbon_9m2", "ss_carbon_9m2", "rt_carbon_9m2", "gv_carbon_9m2")
# 
# lm_pool <- function(c, df) {
#   lm_glm <- summary(lm(formula(paste0("df$", quo_name(c), "~ df$ex_ctrl")), data = df))
#   eval <- eval(lm_glm$call$formula)
#   formula1<- eval(eval)
#   lm_glm$call$formula <- formula1
#   lm_glm
# }
# 
# pools_moose <- lapply(pools, lm_pool, df = c_22_23_moose) # not even the different pools have different carbon
# 
# # try abv and blw
# c_22_23_moose_abv <- c_22_23_moose %>%
#   mutate(c_m2_subplot_agb = (total_c_per_subplot-sl_carbon_9m2)/9)
# c_22_23_moose_blw <- c_22_23_moose %>%
#   mutate(c_m2_subplot_blw = (sl_carbon_9m2)/9)
# 
# summary(lm(c_22_23_moose_abv$c_m2_subplot_agb ~ c_22_23_moose_abv$ex_ctrl)) # almost sig above ground when remove GM_13_2022
# summary(lm(c_22_23_moose_blw$c_m2_subplot_blw ~ c_22_23_moose_blw$ex_ctrl)) # yep super not important
```

## paired exclosure control

## GM
GM exclosures in 2022 only have three subplots
  make fourth out of average of the three others
  also need to tell R which sites are paired
```{r}
# fourth subplot GM exclosures

c_22_23_mooseGM <- c_22_23 %>% 
  filter(ex_ctrl %in% c("CTRL", "EX")) %>% 
  filter(disturbance == "Insect" | disturbance ==  "Mature") %>%
  filter(site_id != "13_2022") %>% # take out 13 because it is a mature exclosure
  filter(park_id == "GM") %>% 
  mutate(new_tot = total_c_per_subplot - dw_carbon_9m2) %>% 
  select(-c(dw_carbon_9m2, total_c_per_subplot)) 

c_cols <- c("dw_carbon_9m2", "te_carbon_9m2", "ll_carbon_9m2", "sl_carbon_9m2", "ss_carbon_9m2", "rt_carbon_9m2", "gv_carbon_9m2", "new_tot") 
dw_c <- c("dw_carbon_9m2")
c_col_lessdw <- setdiff(c_cols, dw_c)

# GM_01_2022
avg_cols_GM01 <- lapply(select(subset(c_22_23_mooseGM, site_id == "01_2022" & ex_ctrl == "EX"), c_col_lessdw), base::mean)

GM_01_2022 <- c(park_id = "GM", site_id = "01_2022", ex_ctrl = "EX", subplot_id = "4", disturbance = "Insect", gap = "Gap", year = 2022, avg_cols_GM01, unique_id = "GM_01_2022_4")
c_22_23_mooseGM <- rbind(c_22_23_mooseGM, GM_01_2022)

# GM_05_2022
avg_cols_GM05 <- lapply(select(subset(c_22_23_mooseGM, site_id == "05_2022" & ex_ctrl == "EX"), c_col_lessdw), base::mean)

GM_05_2022 <- c(park_id = "GM", site_id = "05_2022", ex_ctrl = "EX", subplot_id = "4", disturbance = "Insect", gap = "Gap", year = 2022, avg_cols_GM05, unique_id = "GM_05_2022_4")
c_22_23_mooseGM <- rbind(c_22_23_mooseGM, GM_05_2022)

# GM_13_2022
# this site has insanely large trees in the ctrl which causes the ctrl to have higher c than exlosure
# avg_cols_GM13 <- lapply(select(subset(c_22_23_mooseGM, site_id == "13_2022" & ex_ctrl == "EX"), c_cols), base::mean)
# 
# GM_13_2022 <- c(park_id = "GM", site_id = "13_2022", ex_ctrl = "EX", subplot_id = "4", disturbance = "Insect", gap = "Gap", year = 2022, avg_cols_GM13, unique_id = "GM_13_2022_4")
# c_22_23_mooseGM <- rbind(c_22_23_mooseGM, GM_13_2022)


# give group id
c_22_23_mooseGM <- arrange(c_22_23_mooseGM, unique_id) %>% 
  mutate(pair_id = gl(3,8)) %>% # change 5 to 4 if take out 13_2022
  group_by(pair_id)

# paired test
ex_ctrl_pairGM <- t.test(new_tot ~ ex_ctrl, data = c_22_23_mooseGM, paired = TRUE) # very signififcant once I take out GM 13

c_22_23_mooseGM %>%
  group_by(pair_id) %>%
  summarise(p.value = t.test(new_tot ~ ex_ctrl, paired = TRUE)$p.value) %>%
  ungroup()

# for each pool

lm_pool <- function(c, df) {
  t.test <- t.test(formula(paste0("df$", quo_name(c), "~ df$ex_ctrl")), data = df, paired = TRUE)
}

pools_mooseGM <- lapply(c_col_lessdw, lm_pool, df = c_22_23_mooseGM)
pools_mooseGM # soil shrub & sapling and ground veg not sig

# by above and below
c_22_23_mooseGM_agb <- c_22_23_mooseGM %>%
  mutate(c_m2_subplot_agb = (new_tot-sl_carbon_9m2))
c_22_23_mooseGM_blw <- c_22_23_mooseGM %>%
  mutate(c_m2_subplot_blw = (sl_carbon_9m2))

t.test(c_m2_subplot_agb ~ ex_ctrl, data = c_22_23_mooseGM_agb, paired = TRUE) 
t.test(c_m2_subplot_blw ~ ex_ctrl, data = c_22_23_mooseGM_blw, paired = TRUE) 

# effect of moose overall

c_22_23_mooseGM2 <- c_22_23 %>% 
  filter(ex_ctrl %in% c("CTRL", "EX")) %>% 
  filter(disturbance == "Insect" | disturbance ==  "Mature") %>%
  filter(site_id != "13_2022") %>% # take out 13 because it is a mature exclosure
  filter(park_id == "GM") %>% 
  mutate(new_tot = total_c_per_subplot - dw_carbon_9m2) %>% 
  select(-c(dw_carbon_9m2, total_c_per_subplot)) 

mean_c_mooseGM <- c_22_23_mooseGM2 %>% 
  ungroup() %>% 
  group_by(ex_ctrl) %>% 
  summarize(mean = mean(new_tot/9))

mean_diffGM <- (mean_c_mooseGM$mean[2] - mean_c_mooseGM$mean[1]) # on average effect largely negative
# is per subplot (which is 9m2) so divide by 9 to get per 1 m2


# do I add that to the effect of just insect? I think so: effect of insect + effect of moose in insect
(less_c_insectGM+mean_diffGM)*(7.976e+7)/1000 # wow over a billion kg
```

## TN
```{r}

c_22_23_mooseTN <- c_22_23 %>% 
  filter(ex_ctrl %in% c("CTRL", "EX"))  %>% 
  filter(disturbance == "Insect" | disturbance ==  "Mature") %>%
  filter(site_id != "31_2022" & site_id != "34_2022") %>% # 31 and 34 are mature exclosures
  filter(park_id == "TN") %>% 
  mutate(new_tot = total_c_per_subplot - dw_carbon_9m2) %>% 
  select(-c(dw_carbon_9m2, total_c_per_subplot)) 

# give group id
c_22_23_mooseTN <- arrange(c_22_23_mooseTN, unique_id) %>% 
  mutate(pair_id = gl(5,8)) %>%
  group_by(pair_id)

# paired test
ex_ctrl_pairTN <- t.test(new_tot ~ ex_ctrl, data = c_22_23_mooseTN, paired = TRUE) # not  significantly different


# for each pool
pools_mooseTN <- lapply(c_col_lessdw, lm_pool, df = c_22_23_mooseTN)
pools_mooseTN # litter and ground veg the only sig different

# by above and below
c_22_23_mooseTN_agb <- c_22_23_mooseTN %>%
  mutate(c_m2_subplot_agb = (new_tot-sl_carbon_9m2))
c_22_23_mooseTN_blw <- c_22_23_mooseTN %>%
  mutate(c_m2_subplot_blw = (sl_carbon_9m2))

t.test(c_m2_subplot_agb ~ ex_ctrl, data = c_22_23_mooseTN_agb, paired = TRUE) # above not
t.test(c_m2_subplot_blw ~ ex_ctrl, data = c_22_23_mooseTN_blw, paired = TRUE) # below not

# effect of moose overall

mean_c_mooseTN <- c_22_23_mooseTN %>% 
  ungroup() %>% 
  group_by(ex_ctrl) %>% 
  summarize(mean = mean(new_tot/9))

mean_diffTN <- (mean_c_mooseTN$mean[2] - mean_c_mooseTN$mean[1]) # on average effect is still largely negative. the value is not far off from the value created at GM per m2, but I guess there is just a lot more variation
# is per subplot (which is 9m2) so divide by 9 to get per 1 m2

# is the effect after a disturbance
# this could be interpreted as the amount of carbon moose have stopped from returning in an insect disturbed area
mean_diffTN*(1.3e+7)/1000

# do I add that to the effect of just insect? I think so: effect of insect + effect of moose in insect
(less_c_insectTN+mean_diffTN)*(1.3e+7)/1000
# compare this to value if just look at open plots in mature vs insect
```


```{r}
c_22_23_mooseinsectGM <- c_22_23 %>% 
  filter(park_id == "GM") %>% 
  filter(disturbance == "Insect" | disturbance ==  "Mature") %>% 
  filter(ex_ctrl != "EX")  %>% 
  filter(gap != "Mature" | ex_ctrl != "CTRL")%>% 
  mutate(new_tot = total_c_per_subplot - dw_carbon_9m2) %>% 
  select(-c(dw_carbon_9m2)) 

  
ex_ctrl_pairGM_mi <- t.test(new_tot ~ disturbance, data = c_22_23_mooseinsectGM)


mean_c_miGM <- c_22_23_mooseinsectGM %>% 
  group_by(disturbance) %>% 
  summarize(mean = mean(new_tot/9))

mean_diffGM_mi <- (mean_c_miGM$mean[2] - mean_c_miGM$mean[1])

mean_diffGM_mi - (less_c_insectGM+mean_diffGM) # per m2 difference between calculating together and seperate

mean_diffGM_mi*(1.3e+7)/1000

# diff between this and caluclating effect of insect and moose seperately
mean_diffGM_mi*(1.3e+7)/1000 - (less_c_insectGM+mean_diffGM)*(1.3e+7)/1000
```

```{r}
c_22_23_mooseinsectTN <- c_22_23 %>% 
  filter(park_id == "TN") %>% 
  filter(disturbance == "Insect" | disturbance ==  "Mature") %>% 
  filter(ex_ctrl != "EX")%>% 
  mutate(new_tot = total_c_per_subplot - dw_carbon_9m2) %>% 
  select(-c(dw_carbon_9m2)) 
  
ex_ctrl_pairTN_mi <- t.test(new_tot ~ disturbance, data = c_22_23_mooseinsectTN)

mean_c_miTN <- c_22_23_mooseinsectTN %>% 
  group_by(disturbance) %>% 
  summarize(mean = mean(new_tot/9))

mean_diffTN_mi <- (mean_c_miTN$mean[2] - mean_c_miTN$mean[1])

mean_diffTN_mi - (less_c_insectTN+mean_diffTN) # per m2 difference between calculating together and seperate

mean_diffTN_mi*(1.3e+7)/1000

# diff between this and caluclating effect of insect and moose seperately
mean_diffTN_mi*(1.3e+7)/1000 - (less_c_insectTN+mean_diffTN)*(1.3e+7)/1000
```

```{r}
setdiff(c_22_23_insectGM, select(ungroup(c_22_23_mooseGM), -c(pair_id)))

setdiff(select(c_22_23_mooseinsectGM, -c(total_c_per_subplot)), select(ungroup(c_22_23_mooseGM), -c(pair_id)))


setdiff(c_22_23_insectGM, select(c_22_23_mooseinsectGM, -c(total_c_per_subplot)))


setdiff(c_22_23_insectTN, select(ungroup(c_22_23_mooseTN), -c(pair_id)))

setdiff(select(c_22_23_mooseinsectTN, -c(total_c_per_subplot)), select(ungroup(c_22_23_mooseTN), -c(pair_id)))


setdiff(c_22_23_insectTN, select(c_22_23_mooseinsectTN, -c(total_c_per_subplot)))
```

# diff in excl ctrl vs EVIamp
Either way...could you do the following figure. First, compute abovegroud C in exclosure - aboveground C in control (for each pair). Then maybe just plot that difference for each pair against EVIamp (on y-axis)...or in table? I predict (based on your findings and comment in the markdowns) that we will see higher EVIamp at sites with larger, positive difference in Ex-Ctl.

```{r}


#bring in environmental data
env_subplots_GM <- read_xlsx("/Volumes/Emmerson's backup/C_forecasting_NL_env_data/All in NAD 83 - UTM 21/Sites_and_subplots/env_var/xlsx/to use/env_subplots_GM_final.xlsx") %>% # environmental data from Gros Morne subplots
  rename(CC = "CC15fill")

env_subplots_TN <- read_xlsx("/Volumes/Emmerson's backup/C_forecasting_NL_env_data/All in NAD 83 - UTM 21/Sites_and_subplots/env_var/xlsx/to use/env_subplots_TN_final.xlsx") %>% #environmental data from Terra Nova subplots
    rename(CC = "CC10fill")

env_subplots <- dplyr::bind_rows(env_subplots_TN, env_subplots_GM) 

# make the difference daatframe
c_22_23_moose_diff <- bind_rows(c_22_23_mooseTN, c_22_23_mooseGM) %>% 
  select(park_id, pair_id, subplot_id, ex_ctrl, new_tot) %>% 
  pivot_wider(names_from = ex_ctrl, values_from = new_tot) %>% 
  mutate(diff = EX - CTRL)%>% 
  rename("exC" = EX, "ctrlC" = CTRL)

c_22_23_moose <- rbind(c_22_23_mooseGM, c_22_23_mooseTN)

moose_pair_ex <- inner_join(env_subplots, select(c_22_23_moose, pair_id, site_id, park_id), multiple = "first") %>% 
  select(park_id, subplot_id, ex_ctrl, pair_id, EVIamp)
moose_pair_ex$ex_ctrl <- moose_pair_ex$ex_ctrl %>%
  replace_na("CTRL")
moose_pair_ex <- moose_pair_ex %>% 
  pivot_wider(names_from = ex_ctrl, values_from = EVIamp) %>% 
  mutate(avgEVIamp = (EX+CTRL)/2) %>% 
  rename("exEVIamp" = EX, "ctrlEVIamp" = CTRL)

ex_ctrl_EVIC <- merge(moose_pair_ex, c_22_23_moose_diff)

ggplot(ex_ctrl_EVIC, aes(diff, avgEVIamp)) +
  geom_point()

```


