---
title: "run lmer"
author: "Emmerson Wilson"
date: "2024-01-16"
output:
  word_document:
    toc: true
    toc_depth: '5'
  html_document:
    toc: true
    toc_depth: 5
---

```{r}
pacman::p_load(
  dplyr,
  tidyverse,
  readxl,
  ggplot2,
  vegan,
  terra,
  corrplot,
  PerformanceAnalytics,
  usdm,
  janitor,
  openxlsx,
  lme4,
  DHARMa,
  AICcmodavg,
  boot,
  cv,
  cvms)
```

## data

### c per m2

```{r}
c_per_m2 <- read.xlsx("../final carbon data/c_m2_site.xlsx") %>% 
  rename(unique_id = "id")
c_per_m2_sub <- read.xlsx("../final carbon data/c_m2_subplot.xlsx")
```

### environmental variables at each site

```{r}
env_site_final <- read.xlsx("../final carbon data/env_site_final.xlsx")

dplyr::setdiff(c_per_m2$unique_id, env_site_final$unique_id)

c_env_sites <- full_join(c_per_m2, env_site_final) %>%
  select(!c(FAC, CC, CEC_LCT, dominant))  # remove FAC because super correlated and categorical, remove LGS for now because missing values
  
#subset by park
c_env_sites_GM <- c_env_sites %>% 
  filter(park == "GM")

c_env_sites_TN <- c_env_sites %>% 
  filter(park == "TN")

```

### environmental variables at each subplot

```{r}
env_subplots_final <- read.xlsx("../final carbon data/env_subplots_final.xlsx")

dplyr::setdiff(c_per_m2_sub$unique_id, env_subplots_final$unique_id)

c_env_subplots <- full_join(c_per_m2_sub, env_subplots_final) %>%
  select(!c(FAC, CC, CEC_LCT, SPC))  # remove FAC because super correlated and categorical, remove LGS for now because missing values

#subset by park
c_env_subplots_GM <- c_env_subplots %>% 
  filter(park_id == "GM")

c_env_subplots_TN <- c_env_subplots %>% 
  filter(park_id == "TN")

```

## scale continuous predictor variables

```{r}
c_env_sites_scale <- c_env_sites

c_env_sites_scale[c(11:17)] <- scale(c_env_sites_scale[c(11:17)])

c_env_sites_scale_GM <- c_env_sites_scale %>% 
  filter(park == "GM")

c_env_sites_scale_TN <- c_env_sites_scale %>% 
  filter(park == "TN")
```

#### for subplots

```{r}
c_env_sub_scale <- c_env_subplots

c_env_sub_scale[c(21:27)] <- scale(c_env_sub_scale[c(21:27)])

c_env_sub_scale_GM <- c_env_sub_scale %>% 
  filter(park_id == "GM")

c_env_sub_scale_TN <- c_env_sub_scale %>% 
  filter(park_id == "TN")
```

## cross validation

```{r}
source("")

```

# Model options:

code these as functions in their own script and source("") them in the full document

i\. log(C) \~ **ε**

ii\. log(C) \~ (1\|site) + **ε**

iii\. log(C) \~ all env **ε**

iv\. log(C) \~ all env + (1\|site) + **ε**

v\. log(C) \~ reduced env. + **ε**

vi\. log(C) \~ reduced env. + (1\|site) + **ε**

vii\. log(C) \~ univariate + **ε**

viii\. log(C) \~ univariate + (1\|site) + **ε**

## source models

```{r}
source("lmer model functions.R")
```

## GM

#### by site

##### null

don't actually run code for this - based on significance of other models

##### full

```{r}
full_var <- list("FHT", "EVIamp", "EVImed", "ELE", "SLO", "ASP", "LGS")

GM_lm_full <- lm_full(c_env_sites_scale_GM, "c_m2_site", full_var)
```

##### univariate

```{r}
GM_lm_uni <- lapply(full_var, lm_uni, df = c_env_sites_scale_GM, c = "c_m2_site")


names(GM_lm_uni) <- full_var


```

#### compare

```{r}
GM_models_r <- list()


GM_models_r[["GM_lm_full"]] <- GM_lm_full
GM_models_r[[names(GM_lm_uni)[1]]] <- GM_lm_uni[[1]]
GM_models_r[[names(GM_lm_uni)[2]]] <- GM_lm_uni[[2]]
GM_models_r[[names(GM_lm_uni)[3]]] <- GM_lm_uni[[3]]
GM_models_r[[names(GM_lm_uni)[4]]] <- GM_lm_uni[[4]]
GM_models_r[[names(GM_lm_uni)[5]]] <- GM_lm_uni[[5]]
GM_models_r[[names(GM_lm_uni)[6]]] <- GM_lm_uni[[6]]
GM_models_r[[names(GM_lm_uni)[7]]] <- GM_lm_uni[[7]]

Modnames_GM_r <- paste(names(GM_models_r))

# get table
aictab(cand.set = GM_models_r, modnames = Modnames_GM_r, sort = TRUE)

```

##### reduced

different predictor variables are significant in univariate vs full

at no point are topographic variables important

```{r eval=FALSE, include=FALSE}
GM_red_list <- list("FHT", "EVIamp")

GM_lm_red1 <- lm_red(c_env_sites_scale_GM, "c_m2_site", GM_red_list)

```

#### by subplot

##### null

```{r}
# fixed effects
## doesn't get run as model

# mixed effects
GM_lm_null_site_sub <- lm_null_site(c_env_sub_scale_GM, "c_m2_subplot")
```

##### full

```{r}
# fixed effects

GM_lm_full_sub <- lm_full(c_env_sub_scale_GM, "c_m2_subplot", full_var)

# mixed effects
GM_lm_full_site_sub <- lm_full_site(c_env_sub_scale_GM, "c_m2_subplot", full_var)
```

##### univariate

```{r}
# fixed effects

GM_lm_uni_sub <- lapply(full_var, lm_uni, df = c_env_sub_scale_GM, c = "c_m2_subplot")

names(GM_lm_uni_sub) <- full_var

GM_lm_uni_sub

# mixed effects

GM_lm_uni_site_sub <- lapply(full_var, lm_uni_site, df = c_env_sub_scale_GM, c = "c_m2_subplot")

names(GM_lm_uni_site_sub) <- full_var

GM_lm_uni_site_sub
```

#### compare

```{r}
GM_models_sub_r <- list()

GM_models_sub_r[["GM_lm_full_sub"]] <- GM_lm_full_sub
GM_models_sub_r[[names(GM_lm_uni_sub)[1]]] <- GM_lm_uni_sub[[1]]
GM_models_sub_r[[names(GM_lm_uni_sub)[2]]] <- GM_lm_uni_sub[[2]]
GM_models_sub_r[[names(GM_lm_uni_sub)[3]]] <- GM_lm_uni_sub[[3]]
GM_models_sub_r[[names(GM_lm_uni_sub)[4]]] <- GM_lm_uni_sub[[4]]
GM_models_sub_r[[names(GM_lm_uni_sub)[5]]] <- GM_lm_uni_sub[[5]]
GM_models_sub_r[[names(GM_lm_uni_sub)[6]]] <- GM_lm_uni_sub[[6]]
GM_models_sub_r[[names(GM_lm_uni_sub)[7]]] <- GM_lm_uni_sub[[7]]

Modnames_GM_sub_r <- paste(names(GM_models_sub_r))

# get table
aictab(cand.set = GM_models_sub_r, modnames = Modnames_GM_sub_r, sort = TRUE)

GM_models_site_sub_r <- list()

GM_models_site_sub_r[["GM_lm_null_site_sub"]] <- GM_lm_null_site_sub
GM_models_site_sub_r[["GM_lm_full_site_sub"]] <- GM_lm_full_site_sub
GM_models_site_sub_r[[names(GM_lm_uni_site_sub)[1]]] <- GM_lm_uni_site_sub[[1]]
GM_models_site_sub_r[[names(GM_lm_uni_site_sub)[2]]] <- GM_lm_uni_site_sub[[2]]
GM_models_site_sub_r[[names(GM_lm_uni_site_sub)[3]]] <- GM_lm_uni_site_sub[[3]]
GM_models_site_sub_r[[names(GM_lm_uni_site_sub)[4]]] <- GM_lm_uni_site_sub[[4]]
GM_models_site_sub_r[[names(GM_lm_uni_site_sub)[5]]] <- GM_lm_uni_site_sub[[5]]
GM_models_site_sub_r[[names(GM_lm_uni_site_sub)[6]]] <- GM_lm_uni_site_sub[[6]]
GM_models_site_sub_r[[names(GM_lm_uni_site_sub)[7]]] <- GM_lm_uni_site_sub[[7]]

Modnames_GM_site_sub_r <- paste(names(GM_models_site_sub_r))

# get table
aictab(cand.set = GM_models_site_sub_r, modnames = Modnames_GM_site_sub_r, sort = TRUE)

```

##### reduced

```{r eval=FALSE, include=FALSE}
# fixed effects
GM_red_list_sub <- list("FHT", "LGS")


GM_lm_red1_site <- lm_red(c_env_sub_scale_GM, "c_m2_subplot", GM_red_list_sub)

# mixed effects

GM_lm_red1_site_sub <- lm_red_site(c_env_sub_scale_GM, "c_m2_subplot", GM_red_list_sub)
```

## TN

#### by site

##### null

don't actually run code for this - based on significance of other models

##### full

```{r}
TN_lm_full <- lm_full(c_env_sites_scale_TN, "c_m2_site", full_var)
```

##### univariate

```{r}
TN_lm_uni <- lapply(full_var, lm_uni, df = c_env_sites_scale_TN, c = "c_m2_site")

names(TN_lm_uni) <- full_var

TN_lm_uni
```

#### compare

```{r}
TN_models_r <- list()

TN_models_r[["TN_lm_full"]] <- TN_lm_full
TN_models_r[[names(TN_lm_uni)[1]]] <- TN_lm_uni[[1]]
TN_models_r[[names(TN_lm_uni)[2]]] <- TN_lm_uni[[2]]
TN_models_r[[names(TN_lm_uni)[3]]] <- TN_lm_uni[[3]]
TN_models_r[[names(TN_lm_uni)[4]]] <- TN_lm_uni[[4]]
TN_models_r[[names(TN_lm_uni)[5]]] <- TN_lm_uni[[5]]
TN_models_r[[names(TN_lm_uni)[6]]] <- TN_lm_uni[[6]]
TN_models_r[[names(TN_lm_uni)[7]]] <- TN_lm_uni[[7]]

Modnames_TN_r <- paste(names(TN_models_r))

# get table
aictab(cand.set = TN_models_r, modnames = Modnames_TN_r, sort = TRUE)


```

##### reduced

different predictor variables are significant in univariate vs full

at no point are topographic variables important

```{r eval=FALSE, include=FALSE}
TN_red_list <- list("FHT")

lm_red(c_env_sites_scale_TN, "c_m2_site", TN_red_list)

```

#### by subplot

##### null

```{r}
# fixed effects
## doesn't get run as model

# mixed effects
TN_lm_null_site_sub <- lm_null_site(c_env_sub_scale_TN, "c_m2_subplot")
```

##### full

```{r}
# fixed effects

TN_lm_full_sub <- lm_full(c_env_sub_scale_TN, "c_m2_subplot", full_var)

# mixed effects
TN_lm_full_site_sub <- lm_full_site(c_env_sub_scale_TN, "c_m2_subplot", full_var)
```

##### univariate

```{r}
# fixed effects

TN_lm_uni_sub <- lapply(full_var, lm_uni, df = c_env_sub_scale_TN, c = "c_m2_subplot")

names(TN_lm_uni_sub) <- full_var

TN_lm_uni_sub

# mixed effects

TN_lm_uni_site_sub <- lapply(full_var, lm_uni_site, df = c_env_sub_scale_TN, c = "c_m2_subplot")

names(TN_lm_uni_site_sub) <- full_var

TN_lm_uni_site_sub
```

#### compare

```{r}
TN_models_sub_r <- list()

TN_models_sub_r[["TN_lm_full_sub"]] <- TN_lm_full_sub
TN_models_sub_r[[names(TN_lm_uni_sub)[1]]] <- TN_lm_uni_sub[[1]]
TN_models_sub_r[[names(TN_lm_uni_sub)[2]]] <- TN_lm_uni_sub[[2]]
TN_models_sub_r[[names(TN_lm_uni_sub)[3]]] <- TN_lm_uni_sub[[3]]
TN_models_sub_r[[names(TN_lm_uni_sub)[4]]] <- TN_lm_uni_sub[[4]]
TN_models_sub_r[[names(TN_lm_uni_sub)[5]]] <- TN_lm_uni_sub[[5]]
TN_models_sub_r[[names(TN_lm_uni_sub)[6]]] <- TN_lm_uni_sub[[6]]
TN_models_sub_r[[names(TN_lm_uni_sub)[7]]] <- TN_lm_uni_sub[[7]]

Modnames_TN_sub_r <- paste(names(TN_models_sub_r))

# get table
aictab(cand.set = TN_models_sub_r, modnames = Modnames_TN_sub_r, sort = TRUE)

TN_models_site_sub_r <- list()

TN_models_site_sub_r[["TN_lm_null_site_sub"]] <- TN_lm_null_site_sub
TN_models_site_sub_r[["TN_lm_full_site_sub"]] <- TN_lm_full_site_sub
TN_models_site_sub_r[[names(TN_lm_uni_site_sub)[1]]] <- TN_lm_uni_site_sub[[1]]
TN_models_site_sub_r[[names(TN_lm_uni_site_sub)[2]]] <- TN_lm_uni_site_sub[[2]]
TN_models_site_sub_r[[names(TN_lm_uni_site_sub)[3]]] <- TN_lm_uni_site_sub[[3]]
TN_models_site_sub_r[[names(TN_lm_uni_site_sub)[4]]] <- TN_lm_uni_site_sub[[4]]
TN_models_site_sub_r[[names(TN_lm_uni_site_sub)[5]]] <- TN_lm_uni_site_sub[[5]]
TN_models_site_sub_r[[names(TN_lm_uni_site_sub)[6]]] <- TN_lm_uni_site_sub[[6]]
TN_models_site_sub_r[[names(TN_lm_uni_site_sub)[7]]] <- TN_lm_uni_site_sub[[7]]

Modnames_TN_site_sub_r <- paste(names(TN_models_site_sub_r))

# get table
aictab(cand.set = TN_models_site_sub_r, modnames = Modnames_TN_site_sub_r, sort = TRUE)

```

##### reduced

```{r eval=FALSE, include=FALSE}
# fixed effects
TN_red_list_sub <- list("FHT", "LGS")

lm_red(c_env_sub_scale_TN, "c_m2_subplot", TN_red_list_sub)

# mixed effects

TN_lm_red1_site_sub <- lm_red_site(c_env_sub_scale_TN, "c_m2_subplot", TN_red_list_sub)
```
