---
title: "try_predict"
author: "Emmerson Wilson"
date: "2024-02-05"
output: html_document
---
```{r}
library(terra)
library(tidyverse)
```

```{r}
setwd("~/Documents/Master's/C_forecasting_NL/code_for_stats")
```



trying out predict() function. see how categorical data is handled.
*if moose isn't in any models then probably don't have to worry

use model of GM above ground, log(c) ~ FHT + EVIamp + EVImed + LGS + Moose_new

# model
```{r eval=FALSE, include=FALSE}


GM_model <- lm_glm(GM_var, df = c_agb_env_sites_scale_GM, c = "c_m2_site_agb")
plot(GM_model)
model.frame(GM_model)
summary(GM_model)


crop_extent <- vect("/Users/emmersonEmmerson/Documents/Master's/C_forecasting_NL/Environmental_datasets/AOI/GM_subset_for_predict.shp")
GM_env_raster_crop <- crop(GM_env_raster, crop_extent) # need to run "environmental_correlation.Rmd" first
values(GM_env_raster_crop_scale) <- scale(values(GM_env_raster_crop))


names(GM_env_raster_crop) <-  c("FAC_GM", "EVIamp", "EVImed", "FHT", "CC15fill_GM", "SLO", "ELE", "ASP", "LCT_GM", "Moose_new", "LGS")

plot(GM_env_raster_crop$FHT)
plot(GM_env_raster_crop$EVIamp)
plot(GM_env_raster_crop$EVImed)
plot(GM_env_raster_crop$LGS)

GM_predict <- terra::predict(GM_env_raster_crop, GM_model) # pretty sure predict returns the untransformed values of c *actually it returns the log(c) BUT here I was suing the unscaled environmental variables!
GM_predict0 <- GM_predict
GM_predict0y <- GM_predict

GM_predict0[GM_predict0[] < 0 ] = NA

GM_predict0y[GM_predict0y[] > 0 ] = NA

plot(GM_predict)
plot(GM_predict0)
plot(GM_predict0y) # only a handfull of places that it thinks shoudl be below 0, and I'm pretty sure the EVIampis higher than any of my sites so is clipped out in actual area predicting to - likely because high up so get lots of snow and changes in greeness
```

# model lmer
```{r eval=FALSE, include=FALSE}
GM_var <- list("FHT", "EVImed", "EVIamp", "LGS")

GM_modelm <- lm_lmer(GM_var, df = c_agb_env_sub_scale_GM, c = "c_m2_subplot_agb")
plot(GM_modelm)
model.frame(GM_modelm)
summary(GM_modelm)

GM_predictm <- terra::predict(GM_env_raster_crop, GM_modelm, re.form= ~ 0)
# only way I can get it to work is by making re.form = ~ 0, but this takes away randome variation of site? or predict at the population level? soemthing defenitley happens because the prediction sare different for glm vs lmer

plot(GM_predictm) # slightly constrains the values of C


GM_predictm0 <- GM_predictm
GM_predictm0y <- GM_predictm

GM_predictm0[GM_predictm0[] < 0 ] = NA

GM_predictm0y[GM_predictm0y[] > 0 ] = NA

plot(GM_predictm0)
plot(GM_predictm0y)
```


# try with actual predict space
```{r eval=FALSE, include=FALSE}



GM_env_raster_masked <- rast("/Users/emmersonEmmerson/Documents/Master's/C_forecasting_NL/code_for_stats/tifs for predicting/GM_env_raster_masked.tif")
names(GM_env_raster_masked) <-  c( "FHT", "EVIamp", "EVImed","SLO", "ELE", "ASP", "LGS", "Moose_new",  "Moose_newl",  "Moose_newh",  "Moose_newx")

GM_env_raster_masked_scale <- GM_env_raster_masked
values(GM_env_raster_masked_scale) <- scale(values(GM_env_raster_masked), center = F)

f <- paste0("GM_env_scaled", names(GM_env_raster_masked), ".tif")
writeRaster(GM_env_raster_masked_scale, f, overwrite=TRUE)

GM_var <- list("FHT", "EVImed", "EVIamp", "LGS")

source("https://github.com/emmwilson/C_forecasting_NL/blob/main/code_for_stats/lmer%20model%20functions.R?raw=true")
GM_model <- lm_glm(GM_var, df = c_agb_env_sites_scale_GM, c = "c_m2_site_agb") # need to run c_lmer_aboveground.Tmd first
summary(GM_model)
GM_model$coefficients[1]
GM_model$coefficients[2]
GM_model$coefficients[3]
GM_model$coefficients[4]
GM_model$coefficients[5]

GM_predict <- terra::predict(GM_env_raster_masked_scale, GM_model) # raster calculator gives pretty much the same results (slightly off because precision in R's print is not enough)
GM_predict_transform <- GM_predict
values(GM_predict_transform) <- exp(values(GM_predict))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(GM_predict_transform, background = "lightblue") 

GM_predict_transform60000y <- GM_predict_transform
GM_predict_transform60000y [GM_predict_transform60000y [] < 700000  ] = NA # doesn't actually exist *not sure why legend says it does

GM_predict_transform60000n <- GM_predict_transform

GM_predict_transform60000n [GM_predict_transform60000n [] > 750000  ] = NA

hist(GM_predict_transform60000n)
hist(GM_predict_transform60000y) # all samples are NA so there are no values above 700000, try with lower and lower values
GM_predict_transformhighest <- GM_predict_transform
GM_predict_transformhighest [GM_predict_transformhighest [] < 500000  ] = NA # 3 cells above 500000
hist(GM_predict_transformhighest)


writeRaster(GM_predict_transformhighest, filename="tifs for predicting/trypredict_where_is_large.tif", overwrite=TRUE)
writeRaster(GM_predict_transform, filename="tifs for predicting/trypredict.tif", overwrite=TRUE)
```

# tentative results for presentation

using just FHT for presentation


## GM
problem when I include EVImed - it is highly impacted by shadows
so there is a site with an extremely low EVImed but it is actually a very lush green place it is just in the shadow of a mountain. EVImed is commonly where huge underestimates and overestimates of carbon happen. I only have one site with a very low EVImed and one with a very high EVImed
```{r}
GM_env_raster_masked <- rast("/Users/emmersonEmmerson/Documents/Master's/C_forecasting_NL/code_for_stats/tifs for predicting/GM_env_raster_masked.tif")
names(GM_env_raster_masked) <-  c( "FHT", "EVIamp", "EVImed","SLO", "ELE", "ASP", "LGS", "Moose_new",  "Moose_newl",  "Moose_newh",  "Moose_newx")

GM_env_raster_masked_scale <- GM_env_raster_masked
values(GM_env_raster_masked_scale) <- scale(values(GM_env_raster_masked), center = F) # wrong scaled values


f <- paste0("GM_env_scaled", names(GM_env_raster_masked), ".tif")
writeRaster(GM_env_raster_masked_scale, f, overwrite=TRUE) #export the scaled environmental variable rasters to check predictions usig ratser calculator in qgis

source("https://github.com/emmwilson/C_forecasting_NL/blob/main/code_for_stats/lmer%20model%20functions.R?raw=true")



#trying to predict gap?
try_predict_gap_GM <- glm(as.numeric(gap) ~ FHT + EVIamp, subset(c_env_sites_scale_gap, park_id == "GM"), family = binomial(link = "logit"))
try_predict_gap2_GM <- glm(as.numeric(gap) ~ FHT, subset(c_env_sites_scale_gap, park_id == "GM"), family = binomial(link = "logit"))
try_predict_gap3_GM <- glm(as.numeric(gap) ~ EVIamp, subset(c_env_sites_scale_gap, park_id == "GM"), family = binomial(link = "logit"))
summary(glm(as.numeric(gap) ~ EVImed, subset(c_env_sites_scale_gap, park_id == "TN"), family = binomial(link = "logit")))

summary(try_predict_gap_GM)
AICc(try_predict_gap_GM) # defenitely this
AICc(try_predict_gap2_GM)
AICc(try_predict_gap3_GM)

try_predict_gap1 <- terra::predict(GM_env_raster_masked_scale, try_predict_gap)
values(try_predict_gap1) <- 1 / (1 + exp(-values(try_predict_gap1)))
writeRaster(try_predict_gap1,filename="/Users/emmersonEmmerson/Documents/Master's/C_forecasting_NL/code_for_stats/tifs for predicting/try_predict_gap1.tif")

try_predict_gap_TN <- glm(as.numeric(gap) ~ FHT + EVIamp, subset(c_env_sites_scale_gap, park_id == "TN"), family = binomial(link = "logit"))
try_predict_gap2_TN <- glm(as.numeric(gap) ~ FHT, subset(c_env_sites_scale_gap, park_id == "TN"), family = binomial(link = "logit"))
try_predict_gap3_TN <- glm(as.numeric(gap) ~ EVIamp, subset(c_env_sites_scale_gap, park_id == "TN"), family = binomial(link = "logit"))

summary(try_predict_gap_TN)
AICc(try_predict_gap_TN) # definitely this
AICc(try_predict_gap2_TN)
AICc(try_predict_gap3_TN)

```


### total
```{r}
GM_var_tot <- list("FHT")

GM_model_tot <- lm_glm(GM_var_tot, df = c_env_sites_scale_GM, c = "c_m2_site") # need to run c_lmer_share.Tmd first
summary(GM_model_tot)
GM_model_tot$coefficients[1]
GM_model_tot$coefficients[2]
GM_model_tot$coefficients[3] # print to check predictions in ratsre calculator qgis

GM_predict_tot <- terra::predict(GM_env_raster_masked_scale, GM_model_tot)
GM_predict_tot[GM_predict_tot==NaN] <- NA
GM_predict_tot_transform <- GM_predict_tot
values(GM_predict_tot_transform) <- exp(values(GM_predict_tot))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(GM_predict_tot_transform, background = "lightblue") 

writeRaster(GM_predict_tot_transform, filename="tifs for predicting/GM_predict_tot.tif", overwrite=TRUE)
```


### agb
```{r}
GM_var_agb <- list("FHT")

GM_model_agb <- lm_glm(GM_var_agb, df = c_agb_env_sites_scale_GM, c = "c_m2_site_agb") # need to run c_lmer_aboveground.Tmd first
summary(GM_model_agb)
GM_model_agb$coefficients[1]
GM_model_agb$coefficients[2]
GM_model_agb$coefficients[3] # print to check predictions in ratsre calculator qgis

GM_predict_agb <- terra::predict(GM_env_raster_masked_scale, GM_model_agb)
GM_predict_agb[GM_predict_agb==NaN] <- NA
GM_predict_agb_transform <- GM_predict_agb
values(GM_predict_agb_transform) <- exp(values(GM_predict_agb))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(GM_predict_agb_transform, background = "lightblue") 

writeRaster(GM_predict_agb_transform, filename="tifs for predicting/GM_predict_agb.tif", overwrite=TRUE)



hist(GM_predict_agb_transform)

GM_predict_agb_transformhigh <- GM_predict_agb_transform
GM_predict_agb_transformhigh [GM_predict_agb_transformhigh [] < 4000000  ] = NA
plot(GM_predict_agb_transformhigh)


#just fht to compare to range in TN
GM_var_agb2 <- list("FHT")

GM_model_agb2 <- lm_glm(GM_var_agb2, df = c_agb_env_sites_scale_GM, c = "c_m2_site_agb") # need to run c_lmer_aboveground.Rmd first
summary(GM_model_agb2)
GM_model_agb2$coefficients[1]
GM_model_agb2$coefficients[2]
GM_model_agb2$coefficients[3] # print to check predictions in ratsre calculator qgis

GM_predict_agb2 <- terra::predict(GM_env_raster_masked_scale, GM_model_agb2)
GM_predict_agb2[GM_predict_agb2==NaN] <- NA
GM_predict_agb2_transform <- GM_predict_agb2
values(GM_predict_agb2_transform) <- exp(values(GM_predict_agb2))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(GM_predict_agb2_transform, background = "lightblue") 

writeRaster(GM_predict_agb2_transform, filename="tifs for predicting/GM_predict_agb2.tif", overwrite=TRUE)
```

### blw
```{r}
GM_var_blw <- list(1)

GM_model_blw <- lm_glm(GM_var_blw, df = c_blw_env_sites_scale_GM, c = "c_m2_site_blw") # need to run c_lmer_aboveground.Tmd first
summary(GM_model_blw)
GM_model_blw$coefficients[1]
GM_model_blw$coefficients[2]
GM_model_blw$coefficients[3] # print to check predictions in ratsre calculator qgis

GM_predict_blw <- terra::predict(GM_env_raster_masked_scale, GM_model_blw)
GM_predict_blw_transform <- GM_predict_blw
values(GM_predict_blw_transform) <- exp(values(GM_predict_blw))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(GM_predict_blw_transform, background = "lightblue") 

writeRaster(GM_predict_blw_transform, filename="tifs for predicting/GM_predict_blw.tif", overwrite=TRUE)

# with random effects of site

GM_var_blwr <- list("EVIamp")

GM_model_blwr <- lm_lmer(GM_var_blwr, df = c_blw_env_sub_scale_GM, c = "c_m2_subplot_blw") # need to run c_lmer_aboveground.Tmd first
summary(GM_model_blwr)

GM_predict_blwr <- terra::predict(GM_env_raster_masked_scale, GM_model_blwr, re.form= ~ 0)
GM_predict_blwr[GM_predict_blwr==NaN] <- NA
GM_predict_blwr_transform <- GM_predict_blwr
values(GM_predict_blwr_transform) <- exp(values(GM_predict_blwr))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(GM_predict_blwr_transform, background = "lightblue") 

writeRaster(GM_predict_blwr_transform, filename="tifs for predicting/GM_predict_blwr.tif", overwrite=TRUE)
```


## TN
```{r}
TN_env_raster_masked <- rast("/Users/emmersonEmmerson/Documents/Master's/C_forecasting_NL/code_for_stats/tifs for predicting/TN_env_raster_masked.tif")
names(TN_env_raster_masked) <-  c( "FHT", "EVIamp", "EVImed","SLO", "ELE", "ASP", "LGS", "Moose_new",  "Moose_newl",  "Moose_newh",  "Moose_newx")

TN_env_raster_masked_scale <- TN_env_raster_masked
values(TN_env_raster_masked_scale) <- scale(values(TN_env_raster_masked), center = F)

fTN <- paste0("tifs for predicting/TN_env_scaled", names(TN_env_raster_masked), ".tif")
writeRaster(TN_env_raster_masked_scale, fTN, overwrite=TRUE) #expot the scaled environmental variable rasters to check predictions usig ratser calculator in qgis

```


### total
```{r}
TN_var_tot <- list("FHT")

TN_model_tot <- lm_glm(TN_var_tot, df = c_env_sites_scale_TN, c = "c_m2_site") # need to run c_lmer_aboveground.Tmd first
summary(TN_model_tot)
TN_model_tot$coefficients[1]
TN_model_tot$coefficients[2]
TN_model_tot$coefficients[3] # print to check predictions in ratsre calculator qgis

TN_predict_tot <- terra::predict(TN_env_raster_masked_scale, TN_model_tot)
TN_predict_tot[TN_predict_tot==NaN] <- NA
TN_predict_tot_transform <- TN_predict_tot
values(TN_predict_tot_transform) <- exp(values(TN_predict_tot))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(TN_predict_tot_transform, background = "lightblue") 

writeRaster(TN_predict_tot_transform, filename="tifs for predicting/TN_predict_tot.tif", overwrite=TRUE)
```


### agb
```{r}
TN_var_agb <- list("FHT")

TN_model_agb <- lm_glm(TN_var_agb, df = c_agb_env_sites_scale_TN, c = "c_m2_site_agb") # need to run c_lmer_aboveground.Tmd first
summary(TN_model_agb)
TN_model_agb$coefficients[1]
TN_model_agb$coefficients[2]# print to check predictions in ratsre calculator qgis

TN_predict_agb <- terra::predict(TN_env_raster_masked_scale, TN_model_agb)

TN_predict_agb_transform <- TN_predict_agb
values(TN_predict_agb_transform) <- exp(values(TN_predict_agb))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(TN_predict_agb_transform, background = "lightblue") 

writeRaster(TN_predict_agb_transform, filename="tifs for predicting/TN_predict_agb.tif", overwrite=TRUE)




```

### blw
```{r}
TN_var_blw <- list(1)

TN_model_blw <- lm_glm(TN_var_blw, df = c_blw_env_sites_scale_TN, c = "c_m2_site_blw") # need to run c_lmer_aboveground.Tmd first
summary(TN_model_blw)
TN_model_blw$coefficients[1]
TN_model_blw$coefficients[2]
TN_model_blw$coefficients[3] # print to check predictions in ratsre calculator qgis

TN_predict_blw <- terra::predict(TN_env_raster_masked_scale, TN_model_blw)
TN_predict_blw[TN_predict_blw==NaN] <- NA
TN_predict_blw_transform <- TN_predict_blw
values(TN_predict_blw_transform) <- exp(values(TN_predict_blw))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(TN_predict_blw_transform, background = "lightblue") 

writeRaster(TN_predict_blw_transform, filename="tifs for predicting/TN_predict_blw.tif", overwrite=TRUE)

# with random effects of site

TN_var_blwr <- list("EVIamp")

TN_model_blwr <- lm_lmer(TN_var_blwr, df = c_blw_env_sub_scale_TN, c = "c_m2_subplot_blw") # need to run c_lmer_aboveground.Tmd first
summary(TN_model_blwr)

TN_predict_blwr <- terra::predict(TN_env_raster_masked_scale, TN_model_blwr, re.form= ~ 0)
TN_predict_blwr[TN_predict_blwr==NaN] <- NA
TN_predict_blwr_transform <- TN_predict_blwr
values(TN_predict_blwr_transform) <- exp(values(TN_predict_blwr))*90/1000 # value is c per m2 so can multiply by 90/1000 to get absloute estimate of carbon (not densityt)
plot(TN_predict_blwr_transform, background = "lightblue") 

writeRaster(TN_predict_blwr_transform, filename="tifs for predicting/TN_predict_blwr.tif", overwrite=TRUE)
```

# stats for presentation
```{r}
global(GM_predict_agb2_transform, "mean", na.rm=TRUE) #only show predictions with FHT for now
global(TN_predict_agb_transform, "mean", na.rm=TRUE)

global(GM_predict_agb2_transform, "sum", na.rm=TRUE)
global(TN_predict_agb_transform, "sum", na.rm=TRUE)

global(GM_predict_agb2_transform, "max", na.rm=TRUE)
global(TN_predict_agb_transform, "max", na.rm=TRUE)

global(GM_predict_agb2_transform, "min", na.rm=TRUE)
global(TN_predict_agb_transform, "min", na.rm=TRUE)

```


